### 2021-11-17 Stat 400 proj.Rmd
commit

---
title: "Stat 400 Project"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
incubation_time <- rgamma(5, 6, (2/3))
```

### 2021-11-18 Stat 400 proj.Rmd
crucial distance
created the starting_vals function, and started working on a basic simulation function

@@
 ```{r}
+library(tidyverse)
+
 incubation_time <- rgamma(5, 6, (2/3))
+crucial_distance <- rexp(5, 1/8)
+
+#starter subjects vector
+subjects <- rep('S', 100)
+
+#area grid
+grid_x <- 50
+grid_y <- 50
+
+#starting positions
+start_x <- rep(NA, length(subjects))
+start_y <- rep(NA, length(subjects))
+
+for(i in 1:length(subjects)){
+  start_x[i] <- runif(n=1, min=0, max=grid_x)
+  start_y[i] <- runif(n=1, min=0, max=grid_y)
+}
+
+#plot the starting positions
+ggplot() +
+  geom_point(aes(x=start_x, y=start_y))
+
+#Create df of values for infection status, x coordinate, and y coordinate
+df <- as.data.frame(cbind(subjects, start_x, start_y))
+df$subjects <- as.factor(df$subjects)
+
+#create starting positions function
+starting_vals <- function(num_subjects, x_dim, y_dim){
+
+  start_x <- rep(NA, length(subjects))
+  start_y <- rep(NA, length(subjects))
+
+  for(i in 1:num_subjects){
+  start_x[i] <- runif(n=1, min=0, max=grid_x)
+  start_y[i] <- runif(n=1, min=0, max=grid_y)
+  }
+
+  return(cbind(start_x, start_y))
+}
+
+#simulation function
+simulator <- function(days, num_subjects, x_dim, y_dim){
+  subjects <- rep('S', num_subjects)
+  start_coords <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim)
+  starter_data <- cbind(subjects, start_coords)
+
+}
+
 ```

### 2021-11-22 Stat 400 proj.Rmd
Adding authors
Adding blank function to simluate SIR data, as well as providing df for their reported mc summary data.

@@
 title: "Stat 400 Project"
+authors: "Nathan Hemenway, Mark Hinds, Ian Hall"
 output: pdf_document
@@
 
+#S,I,R data
+suceptable = function(){
+
+}
+
+recovered = function(){
+
+}
+
+infected = function(){
+
+}
+
+#reported monte carlo summary data
+qd = c(0,25,50,75)
+pos = c(99.3,99.2,98.7,92.7)
+dncpv = c(69,53,46,33)
+dncpt = c(26,32,43,42)
+r0 = c(1.8,1.73,1.8,1.63)
+mcsum = cbind(qd,pos,dncpv,dncpt,r0)
+colnames(mcsum,c("Quarantine degree [%]",	"Percentage of size %",	"DNC peak value [cases]",	"DNC peaking time [days]",	"R0"))
 ```

### 2021-11-22 Stat 400 proj.Rmd
Make a more complete starting values function.

--- 2021-11-18 Stat 400 proj.Rmd
@@
 
-#create starting positions function
-starting_vals <- function(num_subjects, x_dim, y_dim){
+#create starting positions and state function
+starting_vals <- function(num_subjects, I_0, x_dim, y_dim){
 
-  start_x <- rep(NA, length(subjects))
-  start_y <- rep(NA, length(subjects))
+  #Storage for x, y starting positions for the subjects
+  start_x <- rep(NA, num_subjects)
+  start_y <- rep(NA, num_subjects)
 
+  #Infect I_0 many starting subjects
+  subjects <- rep('S', num_subjects)
+  infect <- sample(x = 1:num_subjects, size=I_0, replace=FALSE)
+  subjects[infect] <- 'I'
+
+  #Assign starting positions randomly
   for(i in 1:num_subjects){
@@
 
-  return(cbind(start_x, start_y))
+  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects))
+  colnames(df)[1] <- 'x'
+  colnames(df)[2] <- 'y'
+  return(df)
 }
@@
 #simulation function
-simulator <- function(days, num_subjects, x_dim, y_dim){
-  subjects <- rep('S', num_subjects)
-  start_coords <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim)
-  starter_data <- cbind(subjects, start_coords)
+simulator <- function(days, num_subjects, x_dim, y_dim, I_0){
+  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
 

### 2021-11-23 Stat 400 proj.Rmd
Created functions to get step length, step direction, and changes in x,y coordinates.

@@
 
+#Random step length function
+get_step_length <- function(df, x_dim, y_dim){
+  step_lengths <- rnorm(n=nrow(df), mean=min(x_dim, y_dim)/4, sd=min(x_dim, y_dim)/12)
+  return(step_lengths)
+}
+
+#Random step direction function
+get_step_direction <- function(length_vec){
+  direction <- runif(n=length(length_vec), min=0, max=2*pi)
+}
+
+#Get delta_x, delta_y
+get_delts <- function(length_vec, direc_vec){
+  delta_x <- length_vec * cos(direc_vec)
+  delta_y <- length_vec * sin(direc_vec)
+  return(cbind(delta_x, delta_y))
+}
+
 #simulation function
@@
   initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
+
+  for(i in 1:days){
+
+  }
 

### 2021-11-23 Stat 400 proj.Rmd
created a function that gives new x,y coordinates of each individual after a given time period.

@@
   for(i in 1:num_subjects){
-  start_x[i] <- runif(n=1, min=0, max=grid_x)
-  start_y[i] <- runif(n=1, min=0, max=grid_y)
+  start_x[i] <- runif(n=1, min=0, max=x_dim)
+  start_y[i] <- runif(n=1, min=0, max=y_dim)
   }
@@
   return(cbind(delta_x, delta_y))
+}
+
+#Function for getting updated coordinates
+update_coords <- function(og_df, delta_df){
+  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=2)
+  new_df <- data.frame(new_mx)
+  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
+  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
+  colnames(new_df) <- c('x', 'y')
+  return(new_df)
 }

### 2021-11-23 Stat 400 proj.Rmd
Improved/fixed starting_vals and started to create the function for updating infection status.

@@
 
-#starter subjects vector
-subjects <- rep('S', 100)
-
-#area grid
-grid_x <- 50
-grid_y <- 50
-
-#starting positions
-start_x <- rep(NA, length(subjects))
-start_y <- rep(NA, length(subjects))
-
-for(i in 1:length(subjects)){
-  start_x[i] <- runif(n=1, min=0, max=grid_x)
-  start_y[i] <- runif(n=1, min=0, max=grid_y)
-}
-
-#plot the starting positions
-ggplot() +
-  geom_point(aes(x=start_x, y=start_y))
-
-#Create df of values for infection status, x coordinate, and y coordinate
-df <- as.data.frame(cbind(subjects, start_x, start_y))
-df$subjects <- as.factor(df$subjects)
-
 #create starting positions and state function
 starting_vals <- function(num_subjects, I_0, x_dim, y_dim){
-
-  #Storage for x, y starting positions for the subjects
-  start_x <- rep(NA, num_subjects)
-  start_y <- rep(NA, num_subjects)
 
@@
 
-  #Assign starting positions randomly
-  for(i in 1:num_subjects){
-  start_x[i] <- runif(n=1, min=0, max=x_dim)
-  start_y[i] <- runif(n=1, min=0, max=y_dim)
-  }
+  #Storage for x, y starting positions for the subjects
+  start_x <- runif(n=num_subjects, min=0, max=x_dim)
+  start_y <- runif(n=num_subjects, min=0, max=y_dim)
 
+  #Put into a data frame
   df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects))
@@
 
+#Function for deciding if infections occured
+infection_status <- function(state){
+
+  current_infected <- state[state[,'subjects']=='I',]
+  current_suceptable <- state[state[,'subjects']=='S',]
+  current_removed <- state[state[,'subjects']=='R',]
+
+  #Check to see which suceptable subjects get infected
+  crucial_distance <- rexp(n=nrow(coords), 1/8)
+
+  #For loop
+}
+
 #simulation function
@@
 }
+
+#Testing
+df <- starting_vals(100, 2, 10, 10)
+len <- get_step_length(df, 10, 10)
+dir <- get_step_direction(len)
+delts <- get_delts(len, dir)
+newdf <- update_coords(df, delts)
 

### 2021-11-23 Stat 400 proj.Rmd
Got the function deciding if people are close enough to get infected working.

@@
 #Function for deciding if infections occured
-infection_status <- function(state){
+infection_status <- function(state, mean_crit_dist){
 
@@
 
+  #store new infection status
+  new_status <- rep(NA, nrow(current_suceptable))
+
   #Check to see which suceptable subjects get infected
-  crucial_distance <- rexp(n=nrow(coords), 1/8)
-
   #For loop
+  for(i in 1:nrow(current_infected)){
+    for(j in 1:nrow(current_suceptable)){
+      x_i <- as.numeric(current_infected[i, 'x'])
+      y_i <- as.numeric(current_infected[i, 'y'])
+      x_s <- as.numeric(current_suceptable[j, 'x'])
+      y_s <- as.numeric(current_suceptable[j, 'y'])
+      crucial_distance <- rexp(1, 1/mean_crit_dist)
+      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
+      if(d <= crucial_distance){
+        new_status[j] <- 'I'
+      }else{new_status[j] <- 'S'}
+    }
+  }
+  return(new_status)
 }

### 2021-11-25 Stat 400 proj.Rmd
Started getting simulator made, still has issues

@@
 #Function for deciding if infections occured
+#BUG -- If the mean_crit_dist is small, all infections go away!!
 infection_status <- function(state, mean_crit_dist){
 
-  current_infected <- state[state[,'subjects']=='I',]
-  current_suceptable <- state[state[,'subjects']=='S',]
-  current_removed <- state[state[,'subjects']=='R',]
+  current_infected <- state[state[,3]=='I',]
+  current_suceptable <- state[state[,3]=='S',]
+  current_removed <- state[state[,3]=='R',]
 
@@
   initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
+  end_day <- rep(NA, days)
 
@@
 
+    if(i == 1){
+    step_size <- get_step_length(initial_data, x_dim, y_dim)
+    direction <- get_step_direction(step_size)
+    change <- get_delts(step_size, direction)
+    updated_positions <- update_coords(initial_data, change)
+    updated_state <- cbind(updated_positions, initial_data[,3])
+    new_status <- infection_status(updated_state, 2)
+    end_day[i] <- cbind(updated_positions, new_status)
+    }else{
+    step_size <- get_step_length(initial_data, x_dim, y_dim)
+    direction <- get_step_direction(step_size)
+    change <- get_delts(step_size, direction)
+    updated_positions <- update_coords(end_day[i-1], change)
+    updated_state <- cbind(updated_positions, end_day[i-1]$new_status)
+    new_status <- infection_status(updated_state, 1/5)
+    end_day[i] <- cbind(updated_positions, new_status)
+
     }
-
+  }
+  return(end_day)
 }

### 2021-11-25 Stat 400 proj.Rmd
Improved the infection_status function.

@@
   current_removed <- state[state[,3]=='R',]
+  current_non_infected <- rbind(current_suceptable, current_removed)
 
   #store new infection status
-  new_status <- rep(NA, nrow(current_suceptable))
+  new_status <- rep(NA, nrow(current_non_infected))
 
@@
   for(i in 1:nrow(current_infected)){
-    for(j in 1:nrow(current_suceptable)){
+    for(j in 1:nrow(current_non_infected)){
       x_i <- as.numeric(current_infected[i, 'x'])
@@
   }
-  return(new_status)
+  new_state <- c(new_status, current_infected[,3])
+  return(new_state)
 }

### 2021-11-26 Stat 400 proj.Rmd
worked out some problems in simulator function

@@
   initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
-  end_day <- rep(NA, days)
+  end_day <- list()
 
@@
     new_status <- infection_status(updated_state, 2)
-    end_day[i] <- cbind(updated_positions, new_status)
+    end_day[[i]] <- cbind(updated_positions, new_status)
     }else{
@@
     change <- get_delts(step_size, direction)
-    updated_positions <- update_coords(end_day[i-1], change)
-    updated_state <- cbind(updated_positions, end_day[i-1]$new_status)
+    updated_positions <- update_coords(end_day[[i-1]], change)
+    updated_state <- cbind(updated_positions, end_day[[i-1]]$new_status)
     new_status <- infection_status(updated_state, 1/5)
-    end_day[i] <- cbind(updated_positions, new_status)
+    end_day[[i]] <- cbind(updated_positions, new_status)
 
@@
   }
-  return(end_day)
+  return(end_day[[2]])
 }

### 2021-11-29 Stat 400 proj.Rmd
Alternate idea plan, plot, functions, and function shells.

@@
 
-#S,I,R data
-suceptable = function(){
-
-}
-
-recovered = function(){
-
-}
-
-infected = function(){
-
-}
-
 #reported monte carlo summary data
@@
 ```
+
+This method is takes another approach.
+It's somewhat similar to the step function, but this one randomly changes the location of the individuals on a daily basis.
+Then at that point we gather its neighbors and calculate probability of them becoming infected.
+We keep track of those who have come in contact and
+
+``` {r}
+#for knn
+#install.packages('dbscan') 
+library("dbscan")
+```
+
+``` {r}
+#variables
+incubation_time <- rgamma(5, 6, (2/3))
+crucial_distance <- rexp(5, 1/8)
+n = 2000
+starting_infected_prob = 0.005
+
+#starting data and plot
+starting_values = data.frame(cbind(1:n),
+                             cbind(runif(n,0,1),
+                             runif(n,0,1),
+                             rbinom(n,1,starting_infected_prob)),
+                             cbind(rep(0,n)))
+
+colnames(starting_values) = c("id","x","y","infected","susceptible")
+
+#this plot represents the random distribution of 2000 people in a 1km^2 area, with the blue dots being the infected individuals.
+Instead of trying to track progression of time, as the paper illustrates, my thought was to randomize the dot locations each iteration.
+Each iteration represents a day.
+The infected individual will be in another random location each day.
+ggplot() + geom_point(aes(starting_values[,2],starting_values[,3],colour = starting_values[,4])) + xlab("x coordinate") + ylab("y coordinate")
+```
+
+```{r}
+
+#this calculates the distance from an infected individual
+point_dist = function(x1,y1,x2,y2){
+  val = sqrt((x2-x1)^2+(y2-y1)^2)
+  return(val)
+}
+
+#calculates the probability of infection
+#d = current distance from infected, dr = critical value to achieve certain probability of infection
+probability_of_infection = function(d,dr){
+  sigmoid = 1/(1+d*exp(d-dr))
+  return(sigmoid)
+}
+
+#returns data frame of current infected infected individuals
+infected_idx = function(df){
+  idx = df[df$infected==1,]
+  return(idx)
+}
+
+#this function returns a data frame of indexes of people considered susceptible.
+This function aims to calculate the distances of k neighbors then returns a df of indecies of those in neighborhood.
+We will need to keep a running track of the id's of susceptible neighbors and later factor in the probability of becoming infected.
+sus = function(df,idx){
+
+  dist_arr = point_dist(df[,2],df[,3],df[idx,2],df[idx,3])
+  nn = kNN(dist_arr,k = 9)
+  nnidx = nn$id[idx,]
+  return(nnidx)
+}
+
+#estimate the probability one recovers
+recovered = function(df){
+  #lower probability of contracting again
+}
+
+```
+
+``` {r}
+simulator = function(start,b){
+  current_infected = infected_idx(start)
+
+}
+```

### 2021-11-29 Stat 400 proj.Rmd
tried making a coord checker

--- 2021-11-26 Stat 400 proj.Rmd
@@
 
+coord_checker <- function(updated, x_dim, y_dim){
+  num_bads <- 0
+  for(i in 1:nrow(updated)){
+    if(as.numeric(updated[i, 'x']) > x_dim | as.numeric(updated[i, 'y']) > y_dim){
+      new_step <- get_step_length(updated[i,], x_dim, y_dim)
+      new_direction <- get_step_direction(new_step)
+      new_change <- get_delts(new_step, new_direction)
+      # new_df[i,1] <- as.numeric(og_df[i,'x']) + new_change[,'delta_x']
+      # new_df[i,2] <- as.numeric(og_df[i,'y']) + new_change[,'delta_y']
+      updated[i,] <- update_coords(updated[i,], new_change)
+      num_bads <- num_bads + 1
+    }
+  }
+  if(num_bads==0){
+    return(updated)
+  }
+}
+
 #Function for deciding if infections occured
@@
     change <- get_delts(step_size, direction)
-    updated_positions <- update_coords(initial_data, change)
+    updated_positions <- update_coords(initial_data, change, x_dim, y_dim)
     updated_state <- cbind(updated_positions, initial_data[,3])
@@
     change <- get_delts(step_size, direction)
-    updated_positions <- update_coords(end_day[[i-1]], change)
+    updated_positions <- update_coords(end_day[[i-1]], change, x_dim, y_dim)
     updated_state <- cbind(updated_positions, end_day[[i-1]]$new_status)

### 2021-11-30 Stat 400 proj.Rmd
Made *some* progress on step function

--- 2021-11-29 Stat 400 proj.Rmd
@@
   colnames(new_df) <- c('x', 'y')
+
+  baddies <- NULL
+  for(i in 1:nrow(new_df)){
+    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'y']) > y_dim){
+      new_step <- get_step_length(new_df[i,], x_dim, y_dim)
+      new_direction <- get_step_direction(new_step)
+      new_change <- get_delts(new_step, new_direction)
+      new_df[i,] <- update_coords(new_df[i,], new_change)
+      baddies <- append(baddies, i)
+    }
+  }
+}
+
+coord_checker <- function(og_df, new_df, x_dim, y_dim){
+  baddies <- NULL
+  for(i in 1:nrow(new_df)){
+    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'y']) > y_dim){
+      baddies <- append(baddies, i)
+    }
+  }
+
+  if(is.null(baddies)){
     return(new_df)
+  }else{
+  new_step <- get_step_length(new_df[i,], x_dim, y_dim)
+  new_direction <- get_step_direction(new_step)
+  new_change <- get_delts(new_step, new_direction)
+  new_df <- update_coords(og_df[baddies,], new_change)
+  full_df <- rbind(new_df, og_df[-baddies,])
+  return(coord_checker(og_df, full_df, x_dim, y_dim))
+  }
 }
@@
 newdf <- update_coords(df, delts)
+
+#S,I,R data
+suceptable = function(){
+
+}
+
+recovered = function(){
+
+}
+
+infected = function(){
+
+}
 

### 2021-11-30 Stat 400 proj.Rmd
The coord_checker function works, it's just only bounded for positive points.

--- 2021-11-29 Stat 400 proj.Rmd
@@
   colnames(new_df) <- c('x', 'y')
+  new_df
+}
+
+coord_checker <- function(og_df, new_df, x_dim, y_dim){
+  baddies <- NULL
+  for(i in 1:nrow(new_df)){
+    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'y']) > y_dim){
+      baddies <- append(baddies, i)
+    }
+  }
+
+  if(is.null(baddies)){
     return(new_df)
+  }else{
+  new_step <- get_step_length(new_df[i,], x_dim, y_dim)
+  new_direction <- get_step_direction(new_step)
+  new_change <- get_delts(new_step, new_direction)
+  new_df <- update_coords(og_df[baddies,], new_change)
+  full_df <- rbind(new_df, og_df[-baddies, -3])
+  return(coord_checker(og_df, full_df, x_dim, y_dim))
+  }
 }
@@
     change <- get_delts(step_size, direction)
-    updated_positions <- update_coords(initial_data, change)
+    updated_positions <- update_coords(initial_data, change, x_dim, y_dim)
+    # checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
     updated_state <- cbind(updated_positions, initial_data[,3])
@@
 newdf <- update_coords(df, delts)
+coord_checker(df, newdf, 10, 10)
+
+#S,I,R data
+suceptable = function(){
+
+}
+
+recovered = function(){
+
+}
+
+infected = function(){
+
+}
 

### 2021-11-30 Stat 400 proj.Rmd
update infected, more simulator?

--- 2021-11-30 Stat 400 proj.Rmd
@@
 ```{r}
+#testing github
 library(tidyverse)
-
-incubation_time <- rgamma(5, 6, (2/3))
-crucial_distance <- rexp(5, 1/8)
 
@@
 update_coords <- function(og_df, delta_df){
-  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=2)
+  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=3)
   new_df <- data.frame(new_mx)
@@
   new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
-  colnames(new_df) <- c('x', 'y')
+  new_df[,3] <- og_df[,3]
+  colnames(new_df) <- c('x', 'y', 'subjects')
 
-  baddies <- NULL
-  for(i in 1:nrow(new_df)){
-    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'y']) > y_dim){
-      new_step <- get_step_length(new_df[i,], x_dim, y_dim)
-      new_direction <- get_step_direction(new_step)
-      new_change <- get_delts(new_step, new_direction)
-      new_df[i,] <- update_coords(new_df[i,], new_change)
-      baddies <- append(baddies, i)
-    }
-  }
+  new_df
 }
@@
   for(i in 1:nrow(new_df)){
-    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'y']) > y_dim){
+    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'x']) < 0 | as.numeric(new_df[i, 'y']) > y_dim | as.numeric(new_df[i, 'y']) < 0){
       baddies <- append(baddies, i)
@@
   new_status <- rep(NA, nrow(current_non_infected))
+  newly_infected <- NULL
 
@@
         new_status[j] <- 'I'
+        newly_infected <- c(newly_infected, j)
       }else{new_status[j] <- 'S'}
@@
   }
-  new_state <- c(new_status, current_infected[,3])
+
+  current_non_infected[newly_infected, 3] <- 'I'
+  new_state <- rbind(current_infected, current_non_infected)
+
+  # new_state <- c(new_status, current_infected[,3])
   return(new_state)
@@
     change <- get_delts(step_size, direction)
-    updated_positions <- update_coords(initial_data, change, x_dim, y_dim)
-    updated_state <- cbind(updated_positions, initial_data[,3])
-    new_status <- infection_status(updated_state, 2)
-    end_day[[i]] <- cbind(updated_positions, new_status)
+    updated_positions <- update_coords(initial_data, change)
+    checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
+    new_status <- infection_status(checked_positions, 2)
+    checked_positions[,3] <- new_status
+    end_day[[i]] <- checked_positions
+
     }else{
@@
     change <- get_delts(step_size, direction)
-    updated_positions <- update_coords(end_day[[i-1]], change, x_dim, y_dim)
-    updated_state <- cbind(updated_positions, end_day[[i-1]]$new_status)
-    new_status <- infection_status(updated_state, 1/5)
-    end_day[[i]] <- cbind(updated_positions, new_status)
+    updated_positions <- update_coords(end_day[[i-1]], change)
+    checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
+    new_status <- infection_status(checked_positions, 1/5)
+    checked_positions[,3] <- new_status
+    end_day[[i]] <- checked_positions
 
@@
   }
-  return(end_day[[2]])
+  return(end_day[[3]])
 }
@@
 newdf <- update_coords(df, delts)
+coords <- coord_checker(df, newdf, 10, 10)
+coords
+new_status <- infection_status(coords, 2)
+new_status
 
@@
 Then at that point we gather its neighbors and calculate probability of them becoming infected.
-We keep track of those who have come in contact and
+We keep track of their state (and update on if they would become infected or not) - then after a certain duration they heal or die.
+This is computationally easier than having a step function of hundreds of points all moving in space, where we have to calculate distance of each point coming in contact of an infected one.
 

### 2021-11-30 Stat 400 proj.Rmd
commit bug

@@
 
+update_infected = function(indx,state){
+  starting_values[,4] = state
+}
+
+counts = function(day,count){
+  vals = c(day,count)
+  return(vals)
+}
+
 ```
@@
 ``` {r}
-simulator = function(start,b){
+simulator = function(start,b,days){
+  infected_df = cbind(c(1:days),c(rep(NA,days)))
+
+  for(i in 1:days){
     current_infected = infected_idx(start)
+    #list of neighbors close to infected with id, and distance from infected.
+
+    #calculate
+
+  }
 
@@
 ```
+
+```{r}
+
+```

### 2021-11-30 Stat 400 proj.Rmd
Fixed simulation function so that it works with the new coordinate checker function.

--- 2021-11-30 Stat 400 proj.Rmd
@@
 ```{r}
-#testing github
 library(tidyverse)
@@
   for(i in 1:nrow(new_df)){
-    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'x']) < 0 | as.numeric(new_df[i, 'y']) > y_dim | as.numeric(new_df[i, 'y']) < 0){
+    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'y']) > y_dim){
       baddies <- append(baddies, i)
@@
   new_status <- rep(NA, nrow(current_non_infected))
-  newly_infected <- NULL
 
@@
         new_status[j] <- 'I'
-        newly_infected <- c(newly_infected, j)
       }else{new_status[j] <- 'S'}
@@
   }
-
-  current_non_infected[newly_infected, 3] <- 'I'
-  new_state <- rbind(current_infected, current_non_infected)
-
-  # new_state <- c(new_status, current_infected[,3])
+  new_state <- c(new_status, current_infected[,3])
   return(new_state)
@@
 coords <- coord_checker(df, newdf, 10, 10)
-coords
 new_status <- infection_status(coords, 2)
@@
 Then at that point we gather its neighbors and calculate probability of them becoming infected.
-We keep track of their state (and update on if they would become infected or not) - then after a certain duration they heal or die.
-This is computationally easier than having a step function of hundreds of points all moving in space, where we have to calculate distance of each point coming in contact of an infected one.
+We keep track of those who have come in contact and
 

### 2021-12-03 Stat 400 proj.Rmd
test
fix merge conflict

@@
 ```{r}
+#testing github
 library(tidyverse)
@@
 #BUG -- If the mean_crit_dist is small, all infections go away!!
-infection_status <- function(state, mean_crit_dist){
+#BUG -- Sometimes d is NA, I assume it's when indv goes off map. 
+infection_status <- function(state, mean_crit_dist,day_r,rt){
 
@@
 
-  #Check to see which suceptable subjects get infected
+  #Check to see which susceptible subjects get infected
   #For loop
+
   for(i in 1:nrow(current_infected)){
@@
       d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
+
       if(d <= crucial_distance){
         new_status[j] <- 'I'
+
         newly_infected <- c(newly_infected, j)
       }else{new_status[j] <- 'S'}
+
+      }
+
+      #if day is past recovery time, set to recovered
+      else if(day_r >= rt){
+        new_status[j] <- 'R'
+      }
+
+      else{
+        new_status[j] <- 'S'
+      }
+>>>>>>> infection status update
     }
@@
   return(new_state)
+
 }
@@
 
+  recovery_time <- c()
+
   for(i in 1:days){
@@
     change <- get_delts(step_size, direction)
+
     updated_positions <- update_coords(initial_data, change)
@@
 
+    updated_positions <- update_coords(initial_data, change)#, x_dim, y_dim)x_dim,y_dim not parameters
+    # checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
+    updated_state <- cbind(updated_positions, initial_data[,3])
+    new_status <- infection_status(updated_state, 2,i,14)
+    end_day[[i]] <- cbind(updated_positions, new_status)
     }else{
@@
     change <- get_delts(step_size, direction)
+
     updated_positions <- update_coords(end_day[[i-1]], change)
@@
     end_day[[i]] <- checked_positions
+
+    updated_positions <- update_coords(end_day[[i-1]], change)#, x_dim, y_dim) #x_dim,y_dim not parameters in update_coords
+    updated_state <- cbind(updated_positions, end_day[[i-1]]$new_status)
+
+    rand_recovery_time <- rpois(1,14)
+    new_status <- infection_status(updated_state, 1/5,i,rand_recovery_time)
+
+    end_day[[i]] <- cbind(updated_positions, new_status)
 
@@
 
-#S,I,R data
-suceptable = function(){
+x = simulator(100,25,1,1,2)
 
-}
+```
 
-recovered = function(){
+Plots
+``` {r}
+ggplot() + 
+  geom_line(aes())
+```
 
-}
-
-infected = function(){
-
-}
-
+```{r}
 #reported monte carlo summary data
@@
 ```
-
-This method is takes another approach.
-It's somewhat similar to the step function, but this one randomly changes the location of the individuals on a daily basis.
-Then at that point we gather its neighbors and calculate probability of them becoming infected.
-We keep track of those who have come in contact and
-
-``` {r}
-#for knn
-#install.packages('dbscan') 
-library("dbscan")
-```
-
-``` {r}
-#variables
-incubation_time <- rgamma(5, 6, (2/3))
-crucial_distance <- rexp(5, 1/8)
-n = 2000
-starting_infected_prob = 0.005
-
-#starting data and plot
-starting_values = data.frame(cbind(1:n),
-                             cbind(runif(n,0,1),
-                             runif(n,0,1),
-                             rbinom(n,1,starting_infected_prob)),
-                             cbind(rep(0,n)))
-
-colnames(starting_values) = c("id","x","y","infected","susceptible")
-
-#this plot represents the random distribution of 2000 people in a 1km^2 area, with the blue dots being the infected individuals.
-Instead of trying to track progression of time, as the paper illustrates, my thought was to randomize the dot locations each iteration.
-Each iteration represents a day.
-The infected individual will be in another random location each day.
-ggplot() + geom_point(aes(starting_values[,2],starting_values[,3],colour = starting_values[,4])) + xlab("x coordinate") + ylab("y coordinate")
-```
-
-```{r}
-
-#this calculates the distance from an infected individual
-point_dist = function(x1,y1,x2,y2){
-  val = sqrt((x2-x1)^2+(y2-y1)^2)
-  return(val)
-}
-
-#calculates the probability of infection
-#d = current distance from infected, dr = critical value to achieve certain probability of infection
-probability_of_infection = function(d,dr){
-  sigmoid = 1/(1+d*exp(d-dr))
-  return(sigmoid)
-}
-
-#returns data frame of current infected infected individuals
-infected_idx = function(df){
-  idx = df[df$infected==1,]
-  return(idx)
-}
-
-#this function returns a data frame of indexes of people considered susceptible.
-This function aims to calculate the distances of k neighbors then returns a df of indecies of those in neighborhood.
-We will need to keep a running track of the id's of susceptible neighbors and later factor in the probability of becoming infected.
-sus = function(df,idx){
-
-  dist_arr = point_dist(df[,2],df[,3],df[idx,2],df[idx,3])
-  nn = kNN(dist_arr,k = 9)
-  nnidx = nn$id[idx,]
-  return(nnidx)
-}
-
-#estimate the probability one recovers
-recovered = function(df){
-  #lower probability of contracting again
-}
-
-```
-
-``` {r}
-simulator = function(start,b){
-  current_infected = infected_idx(start)
-
-}
-```

### 2021-12-03 Stat 400 proj.Rmd
Trying to fix merge conflict
fix merge conflict

@@
 #BUG -- Sometimes d is NA, I assume it's when indv goes off map. 
-infection_status <- function(state, mean_crit_dist,day_r,rt){
+infection_status <- function(state, mean_crit_dist){
 
@@
         new_status[j] <- 'I'
+        newly_infected <- c(newly_infected, j)
+      }
+      else{new_status[j] <- 'S'}
 
-        newly_infected <- c(newly_infected, j)
-      }else{new_status[j] <- 'S'}
-
-      }
-
-      #if day is past recovery time, set to recovered
-      else if(day_r >= rt){
-        new_status[j] <- 'R'
       }
@@
       }
->>>>>>> infection status update
     }
@@
   return(new_state)
-
-}
 
@@
       updated_state <- cbind(updated_positions, initial_data[,3])
-    new_status <- infection_status(updated_state, 2,i,14)
+
+      new_status <- infection_status(updated_state, 2)
+
       end_day[[i]] <- cbind(updated_positions, new_status)
-    }else{
+    }
+    else{
       step_size <- get_step_length(initial_data, x_dim, y_dim)
@@
       end_day[[i]] <- cbind(updated_positions, new_status)
-
     }

### 2021-12-04 Stat 400 proj.Rmd

@@
       }
-      else{new_status[j] <- 'S'}
-
-      }
-
       else{
@@
   return(new_state)
+}
 

### 2021-12-04 Stat 400 proj.Rmd
Created new columns for incubation and recovery time and assign each new infection one in the infection status function.

@@
 
+  #Create null incubation and recovery time columns
+  inc_time <- rep(NA, num_subjects)
+  rec_time <- rep(NA, num_subjects)
+
   #Put into a data frame
-  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects))
+  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects, inc_time, rec_time))
   colnames(df)[1] <- 'x'
   colnames(df)[2] <- 'y'
+  colnames(df)[4] <- 'inc_time'
+  colnames(df)[5] <- 'rec_time'
   return(df)
@@
 update_coords <- function(og_df, delta_df){
-  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=3)
+  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=5)
   new_df <- data.frame(new_mx)
@@
   new_df[,3] <- og_df[,3]
-  colnames(new_df) <- c('x', 'y', 'subjects')
+  new_df[,4] <- og_df[,4]
+  new_df[,5] <- og_df[,5]
+  colnames(new_df) <- c('x', 'y', 'subjects', 'incubation', 'recovery')
 
@@
 
-  #store new infection status
-  new_status <- rep(NA, nrow(current_non_infected))
+  #store vector of newly infecteds
   newly_infected <- NULL
@@
       if(d <= crucial_distance){
-        new_status[j] <- 'I'
         newly_infected <- c(newly_infected, j)
-      }
-      else{
-        new_status[j] <- 'S'
       }
@@
   current_non_infected[newly_infected, 3] <- 'I'
+  #Give an incubation time
+  current_non_infected[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 14)
+
+  #Give a recovery time
+  current_non_infected[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)
+
   new_state <- rbind(current_infected, current_non_infected)
-
-  # new_state <- c(new_status, current_infected[,3])
   return(new_state)

### 2021-12-04 Stat 400 proj.Rmd
update infection status function with added recovery times

--- 2021-12-04 Stat 400 proj.Rmd
@@
 
+  #generated days of recovery times for each person
+  recovery_days <- rpois(num_subjects,14)
+
   #Put into a data frame
-  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects))
+  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects,recovery_days))
   colnames(df)[1] <- 'x'
@@
 
-#Function for deciding if infections occured
+#Function for deciding if infections occurred
 #BUG -- If the mean_crit_dist is small, all infections go away!!
-#BUG -- Sometimes d is NA, I assume it's when indv goes off map. 
-infection_status <- function(state, mean_crit_dist){
+infection_status <- function(state, mean_crit_dist,t){
 
@@
   current_removed <- state[state[,3]=='R',]
+
+  current_recovered <- state[state[,3]=='Rec',]
+
   current_non_infected <- rbind(current_suceptable, current_removed)
@@
       y_s <- as.numeric(current_suceptable[j, 'y'])
+
+      z_s <- as.numeric(current_recovered[i,'Rec'])
+
       crucial_distance <- rexp(1, 1/mean_crit_dist)
@@
         newly_infected <- c(newly_infected, j)
+      }
+      #check recovery time for person at z_s
+      if(z_s>=t){
+        new_status[j] <- 'Rec'
       }
@@
   return(new_state)
+}
+
+get_recovery_time <- function(){
+
 }
@@
 
+      r_times <-
+
       updated_positions <- update_coords(initial_data, change)
       checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
-      new_status <- infection_status(checked_positions, 2)
+      new_status <- infection_status(checked_positions, 2,i)
       checked_positions[,3] <- new_status
@@
       checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
-      new_status <- infection_status(checked_positions, 1/5)
+      new_status <- infection_status(checked_positions, 1/5,i)
       checked_positions[,3] <- new_status

### 2021-12-04 Stat 400 proj.Rmd
recovery time comments

@@
   colnames(df)[2] <- 'y'
+  colnames(df)[3] <- 'recovery_times'
   return(df)
@@
 
-      r_times <-
+      r_times <- get_recovery()
 

### 2021-12-04 Stat 400 proj.Rmd
bugs

--- 2021-12-04 Stat 400 proj.Rmd
@@
 
-  #generated days of recovery times for each person
+  #pregenerated days of recovery times for each person
   recovery_days <- rpois(num_subjects,14)
+  inc_time <- rpois(num_subjects,5)
 
   #Put into a data frame
-  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects,recovery_days))
+  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects,recovery_days,inc_time))
   colnames(df)[1] <- 'x'
   colnames(df)[2] <- 'y'
+  colnames(df)[3] <- 'subjects'
+  colnames(df)[4] <- 'recovery'
+  colnames(df)[5] <- 'incubation'
   return(df)
@@
   new_df[,3] <- og_df[,3]
-  colnames(new_df) <- c('x', 'y', 'subjects')
-
+  new_df[,4] <- og_df[,4]
+  new_df[,5] <- og_df[,5]
+  colnames(new_df) <- c('x', 'y', 'subjects', 'recovery', 'incubation')
   new_df
@@
 
-  current_recovered <- state[state[,3]=='Rec',]
+  current_non_infected <- rbind(current_suceptable, current_removed)
 
-  current_non_infected <- rbind(current_suceptable, current_removed)
+  #is this right do get the list of recovery days?
+  current_rec_time <- state[state[,4]]
 
@@
 
-      z_s <- as.numeric(current_recovered[i,'Rec'])
+      z_s <- as.numeric(current_rec_time[i])
 
@@
       }
-      #check recovery time for person at z_s
+
+      #check recovery time for person at z_s. If their recovery day time is past the current day, they recovered. 
       if(z_s>=t){
@@
       }
+
       else{
@@
 
-get_recovery_time <- function(){
-
-}
-
 #simulation function
@@
 
-  recovery_time <- c()
+  recovery_time <- initial_data[,4]
 
@@
       change <- get_delts(step_size, direction)
-
-      r_times <-
 

### 2021-12-04 Stat 400 proj.Rmd
fix indexing for recovery df?

@@
   start_y <- runif(n=num_subjects, min=0, max=y_dim)
+
+  #Create null incubation and recovery time columns
+  #inc_time <- rep(NA, num_subjects)
+  #rec_time <- rep(NA, num_subjects)
 
@@
 #BUG -- If the mean_crit_dist is small, all infections go away!!
-infection_status <- function(state, mean_crit_dist,t){
+
+#t = the current day, rt is df of recovery times. 
+infection_status <- function(state, mean_crit_dist,t,rt){
 
@@
   current_non_infected <- rbind(current_suceptable, current_removed)
-
-  #is this right do get the list of recovery days?
-  current_rec_time <- state[state[,4]]
 
@@
 
-      z_s <- as.numeric(current_rec_time[i])
+      #day of recovery for current infected
+      z_s <- as.numeric(rt[i])
 
@@
 
-      else{
-        new_status[j] <- 'S'
-      }
+      #else{
+       # new_status[j] <- 'S'
+      #}
     }
@@
 
-  current_non_infected[newly_infected, 3] <- 'I'
   new_state <- rbind(current_infected, current_non_infected)
-
-  # new_state <- c(new_status, current_infected[,3])
   return(new_state)
@@
       checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
-      new_status <- infection_status(checked_positions, 2,i)
+      new_status <- infection_status(checked_positions, 2,i,recovery_time)
       checked_positions[,3] <- new_status
@@
 
-      new_status <- infection_status(updated_state, 2)
+      new_status <- infection_status(updated_state, 2,i,recovery_time)
 
@@
       checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
-      new_status <- infection_status(checked_positions, 1/5,i)
+      new_status <- infection_status(checked_positions, 1/5,i,recovery_time)
       checked_positions[,3] <- new_status
@@
       rand_recovery_time <- rpois(1,14)
-      new_status <- infection_status(updated_state, 1/5,i,rand_recovery_time)
+      new_status <- infection_status(updated_state, 1/5,i,recovery_time)
 
@@
 coords <- coord_checker(df, newdf, 10, 10)
-new_status <- infection_status(coords, 2)
-new_status
+#new_status <- infection_status(coords, 2)
+#new_status
 

### 2021-12-04 Stat 400 proj.Rmd
added more of nates code that didn't pull
it says i need to commit
basic recovery time update

--- 2021-12-04 Stat 400 proj.Rmd
@@
 
-  #pregenerated days of recovery times for each person
-  recovery_days <- rpois(num_subjects,14)
-  inc_time <- rpois(num_subjects,5)
+  #Create null incubation and recovery time columns
+  #inc_time <- rep(NA, num_subjects)
+  #rec_time <- rep(NA, num_subjects)
+
+  inc_time <- rep(-1,num_subjects)
+  rec_days <- rep(-1,num_subjects)
 
@@
   colnames(df)[3] <- 'subjects'
-  colnames(df)[4] <- 'recovery'
-  colnames(df)[5] <- 'incubation'
+  colnames(df)[4] <- 'incubation'
+  colnames(df)[5] <- 'recovery'
   return(df)
@@
 #BUG -- If the mean_crit_dist is small, all infections go away!!
-infection_status <- function(state, mean_crit_dist,t){
+
+#t = the current day, rt is df of recovery times. 
+infection_status <- function(state, mean_crit_dist){
 
@@
 
-      z_s <- as.numeric(current_rec_time[i])
-
       crucial_distance <- rexp(1, 1/mean_crit_dist)
@@
       if(d <= crucial_distance){
-        new_status[j] <- 'I'
         newly_infected <- c(newly_infected, j)
-      }
-
-      #check recovery time for person at z_s. If their recovery day time is past the current day, they recovered. 
-      if(z_s>=t){
-        new_status[j] <- 'Rec'
-      }
-
-      else{
-        new_status[j] <- 'S'
       }
@@
   }
-
   current_non_infected[newly_infected, 3] <- 'I'
+  current_non_infected[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5)
+  current_non_infected[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)
   new_state <- rbind(current_infected, current_non_infected)
-
-  # new_state <- c(new_status, current_infected[,3])
   return(new_state)
@@
       checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
-      new_status <- infection_status(checked_positions, 2,i)
-      checked_positions[,3] <- new_status
-      end_day[[i]] <- checked_positions
+      new_status <- infection_status(checked_positions, 2)
 
-      updated_positions <- update_coords(initial_data, change)#, x_dim, y_dim)x_dim,y_dim not parameters
-      # checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
-      updated_state <- cbind(updated_positions, initial_data[,3])
+      not_recovered = new_status[new_status[,5]>=0]
+      other = new_status[new_status[,5]<0]
 
-      new_status <- infection_status(updated_state, 2)
+      new_status = rbind(non_recovered[,5]-1,other)
 
-      end_day[[i]] <- cbind(updated_positions, new_status)
+      end_day[[i]] <- new_status
+
     }
+
     else{
@@
       checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
-      new_status <- infection_status(checked_positions, 1/5,i)
-      checked_positions[,3] <- new_status
-      end_day[[i]] <- checked_positions
+      new_status <- infection_status(checked_positions, 1/5)
 
-      updated_positions <- update_coords(end_day[[i-1]], change)#, x_dim, y_dim) #x_dim,y_dim not parameters in update_coords
-      updated_state <- cbind(updated_positions, end_day[[i-1]]$new_status)
+      not_recovered = new_status[new_status[,5]>=0]
+      other = new_status[new_status[,5]<0]
 
-      rand_recovery_time <- rpois(1,14)
-      new_status <- infection_status(updated_state, 1/5,i,rand_recovery_time)
+      new_status = rbind(non_recovered[,5]-1,other)
 
-      end_day[[i]] <- cbind(updated_positions, new_status)
+      end_day[[i]] <- new_status
+
     }

### 2021-12-04 Stat 400 proj.Rmd
Need to fix infection status error

@@
 
-  #Create null incubation and recovery time columns
-  #inc_time <- rep(NA, num_subjects)
-  #rec_time <- rep(NA, num_subjects)
-
   inc_time <- rep(-1,num_subjects)
@@
   #Put into a data frame
-  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects,recovery_days,inc_time))
+  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects, rec_days, inc_time))
   colnames(df)[1] <- 'x'
@@
 #BUG -- If the mean_crit_dist is small, all infections go away!!
-
-#t = the current day, rt is df of recovery times. 
 infection_status <- function(state, mean_crit_dist){
@@
       y_i <- as.numeric(current_infected[i, 'y'])
-      x_s <- as.numeric(current_suceptable[j, 'x'])
-      y_s <- as.numeric(current_suceptable[j, 'y'])
+      x_s <- as.numeric(current_non_infected[j, 'x'])
+      y_s <- as.numeric(current_non_infected[j, 'y'])
 
@@
       d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
-
+      print(c(d <= crucial_distance, x_i, x_s))
       if(d <= crucial_distance){
@@
       }
+
     }
@@
   current_non_infected[newly_infected, 3] <- 'I'
+  #Give incubation time
   current_non_infected[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5)
+  #Give recovery time
   current_non_infected[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)
+
   new_state <- rbind(current_infected, current_non_infected)
@@
   end_day <- list()
-
-  recovery_time <- initial_data[,4]
 
@@
       checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
+      print(checked_positions)
       new_status <- infection_status(checked_positions, 2)
 
-      not_recovered = new_status[new_status[,5]>=0]
-      other = new_status[new_status[,5]<0]
+      not_recovered = new_status[new_status[, 5] > 0]
+      new_time <- not_recovered[, 5] - 1
+      not_recovered[, 5] <- new_time
+      infected_0 <- new_status[new_status[, 5] == 0]
+      infected_0[, 3] <- 'R'
+      not_infected = new_status[new_status[, 5] < 0]
 
-      new_status = rbind(non_recovered[,5]-1,other)
-
+      new_status = rbind(not_recovered, infected_0, not_infected)
       end_day[[i]] <- new_status
@@
       checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
-      new_status <- infection_status(checked_positions, 1/5)
+      new_status <- infection_status(checked_positions, 5)
 
-      not_recovered = new_status[new_status[,5]>=0]
-      other = new_status[new_status[,5]<0]
+      not_recovered = new_status[new_status[, 5] > 0]
+      new_time <- not_recovered[, 5] - 1
+      not_recovered[, 5] <- new_time
+      infected_0 <- new_status[new_status[, 5] == 0]
+      infected_0[, 3] <- 'R'
+      not_infected = new_status[new_status[, 5] < 0]
 
-      new_status = rbind(non_recovered[,5]-1,other)
-
+      new_status = rbind(not_recovered, infected_0, not_infected)
       end_day[[i]] <- new_status

### 2021-12-05 Stat 400 proj.Rmd
Fixed simulation error, turns out it didnt make sense to see which sus ppl get infected when theres no sus ppl

@@
 
-  current_non_infected <- rbind(current_suceptable, current_removed)
-
   #store new infection status
-  new_status <- rep(NA, nrow(current_non_infected))
   newly_infected <- NULL
@@
   #For loop
-
+  if(nrow(current_suceptable) != 0){
   for(i in 1:nrow(current_infected)){
-    for(j in 1:nrow(current_non_infected)){
+    for(j in 1:nrow(current_suceptable)){
       x_i <- as.numeric(current_infected[i, 'x'])
       y_i <- as.numeric(current_infected[i, 'y'])
-      x_s <- as.numeric(current_non_infected[j, 'x'])
-      y_s <- as.numeric(current_non_infected[j, 'y'])
+      x_s <- as.numeric(current_suceptable[j, 'x'])
+      y_s <- as.numeric(current_suceptable[j, 'y'])
 
@@
       d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
-      print(c(d <= crucial_distance, x_i, x_s))
+      # print(c(d <= crucial_distance, x_i, x_s, j, i, nrow(current_infected)))
       if(d <= crucial_distance){
@@
   }
-  current_non_infected[newly_infected, 3] <- 'I'
+
+  current_suceptable[newly_infected, 3] <- 'I'
   #Give incubation time
-  current_non_infected[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5)
+  current_suceptable[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5)
   #Give recovery time
-  current_non_infected[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)
+  current_suceptable[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)
 
-  new_state <- rbind(current_infected, current_non_infected)
+  new_state <- rbind(current_infected, current_suceptable, current_removed)
   return(new_state)
+  }else{return(state)}
 }
@@
       checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
-      print(checked_positions)
       new_status <- infection_status(checked_positions, 2)
 
-      not_recovered = new_status[new_status[, 5] > 0]
-      new_time <- not_recovered[, 5] - 1
+      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
+      new_time <- as.numeric(not_recovered[, 5]) - 1
       not_recovered[, 5] <- new_time
-      infected_0 <- new_status[new_status[, 5] == 0]
-      infected_0[, 3] <- 'R'
-      not_infected = new_status[new_status[, 5] < 0]
+      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
+      infected_0[, 3] <- rep('R', nrow(infected_0))
+      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
 
@@
 
-      not_recovered = new_status[new_status[, 5] > 0]
-      new_time <- not_recovered[, 5] - 1
+      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
+      new_time <- as.numeric(not_recovered[, 5]) - 1
       not_recovered[, 5] <- new_time
-      infected_0 <- new_status[new_status[, 5] == 0]
-      infected_0[, 3] <- 'R'
-      not_infected = new_status[new_status[, 5] < 0]
+      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
+      infected_0[, 3] <- rep('R', nrow(infected_0))
+      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
 
@@
   }
-  return(end_day[[3]])
+  return(end_day[[1]])
 }
@@
 #Testing
-df <- starting_vals(100, 2, 10, 10)
-len <- get_step_length(df, 10, 10)
+df <- starting_vals(10, 2, 1, 1)
+len <- get_step_length(df, 1, 1)
 dir <- get_step_direction(len)
@@
 newdf <- update_coords(df, delts)
-coords <- coord_checker(df, newdf, 10, 10)
+coords <- coord_checker(df, newdf, 1, 1)
+coords
 new_status <- infection_status(coords, 2)

### 2021-12-05 Stat 400 proj.Rmd
We have a graph!

@@
 
-  inc_time <- rep(-1,num_subjects)
-  rec_days <- rep(-1,num_subjects)
+  inc_time <- rep(-1, num_subjects)
+  rec_days <- rep(-1, num_subjects)
 
@@
   colnames(df)[5] <- 'recovery'
+
+  #Assign a recovery time to the infected subjects
+  df[df[,3] == 'I', 5] <- rpois(I_0, 14)
+
+  #Assign an incubation time to the infected subjects
+  df[df[,3] == 'I', 4] <- rpois(I_0, 5)
+
   return(df)
@@
   new_df[,5] <- og_df[,5]
-  colnames(new_df) <- c('x', 'y', 'subjects', 'recovery', 'incubation')
+  colnames(new_df) <- c('x', 'y', 'subjects', 'incubation', 'recovery')
   new_df
@@
 #simulation function
-simulator <- function(days, num_subjects, x_dim, y_dim, I_0){
+simulator <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist){
   initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
   end_day <- list()
+  num_cases <- rep(NA, days)
+  num_cases <- c(I_0, num_cases)
+  num_new_cases <- rep(NA, days)
 
@@
       checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
-      new_status <- infection_status(checked_positions, 2)
+      new_status <- infection_status(checked_positions, inf_dist)
 
@@
 
+      #Calculate number of new cases
+      num_cases[i+1] <- sum(new_status[,3]=='I')
+      num_new_cases[i] <- sum(new_status[,3]=='I') - I_0
+
     }
@@
       checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
-      new_status <- infection_status(checked_positions, 5)
+      new_status <- infection_status(checked_positions, inf_dist)
 
@@
 
+      #Calculate number of new cases
+      num_cases[i+1] <- sum(new_status[,3]=='I')
+      num_new_cases[i] <- sum(new_status[,3]=='I') - num_cases[i-1]
+
     }
   }
-  return(end_day[[1]])
+  return(num_cases)
 }
@@
 
-x = simulator(100,25,1,1,2)
+y <- simulator(30,25,10,10,2,1)
+x <- 0:30
+
+library(ggplot2)
+ggplot() +
+  geom_line(aes(x=x, y=y)) +
+  xlab('Day') +
+  ylab('Number of Cases') +
+  ggtitle('Number of Covid-19 cases over time')
 

### 2021-12-06 Stat 400 proj.Rmd
Added bootstrap function

@@
 knitr::opts_chunk$set(echo = TRUE)
+#testing github
+library(tidyverse)
+library(ggplot2)
+library(boot)
 ```
@@
 ```{r}
-#testing github
-library(tidyverse)
 
@@
       crucial_distance <- rexp(1, 1/mean_crit_dist)
+
       d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
-      # print(c(d <= crucial_distance, x_i, x_s, j, i, nrow(current_infected)))
       if(d <= crucial_distance){
@@
 
-y <- simulator(30,25,10,10,2,1)
-x <- 0:30
+n=100
+y <- simulator(n,100,10,10,2,1)
+x <- 0:n
 
-library(ggplot2)
 ggplot() +
@@
 
-```
+#bootstrap
 
-Plots
-``` {r}
-ggplot() + 
-  geom_line(aes())
+mean_func <- function(x, idx) {
+  mean(x[idx])
+}
+
+daily_cases <- y
+boot.case <- boot(daily_cases, mean_func, 2000)
+
+plot(boot.case)
+
+boot.ci(boot.case, conf = .95, type = c("perc", "basic", "norm", "bca"))
+
 ```
@@
 colnames(mcsum,c("Quarantine degree [%]",	"Percentage of size %",	"DNC peak value [cases]",	"DNC peaking time [days]",	"R0"))
+mcsum
 ```

### 2021-12-06 Stat 400 proj.Rmd
Got incubation to work

@@
 #Function for deciding if infections occurred
-#BUG -- If the mean_crit_dist is small, all infections go away!!
 infection_status <- function(state, mean_crit_dist){
 
-  current_infected <- state[state[,3]=='I',]
+  current_infected <- state[state[,3]=='I' & state[,4] <= 0,]
   current_suceptable <- state[state[,3]=='S',]
   current_removed <- state[state[,3]=='R',]
+  current_non_contagious <- state[state[,3]=='I' & state[,4] > 0,]
 
@@
   #For loop
-  if(nrow(current_suceptable) != 0){
+  if(nrow(current_suceptable) != 0 & nrow(current_infected) != 0){
   for(i in 1:nrow(current_infected)){
@@
 
-  new_state <- rbind(current_infected, current_suceptable, current_removed)
+  new_state <- rbind(current_infected, current_suceptable, current_removed, current_non_contagious)
   return(new_state)
@@
 
+      #recovery time code
       not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
@@
       not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
+      new_status = rbind(not_recovered, infected_0, not_infected)
 
-      new_status = rbind(not_recovered, infected_0, not_infected)
+      #incubation time code
+      infected_people <- new_status[new_status[,3] == 'I',]
+      new_inc_time <- as.numeric(infected_people[,4]) - 1
+      infected_people[,4] <- new_inc_time
+      other_people <- new_status[new_status[,3] != 'I',]
+      new_status <- rbind(infected_people, other_people)
+      print(infected_people)
+
       end_day[[i]] <- new_status
@@
 #Testing
-df <- starting_vals(10, 2, 1, 1)
+df <- starting_vals(1000, 2, 1, 1)
 len <- get_step_length(df, 1, 1)
@@
 coords
-new_status <- infection_status(coords, 2)
+new_status <- infection_status(coords, 8)
 new_status
+print(new_status[,4])
 
-n=100
+set.seed(400)
+n=50
 y <- simulator(n,100,10,10,2,1)
@@
 
-ggplot() +
+plot <- ggplot() +
   geom_line(aes(x=x, y=y)) +

### 2021-12-07 Stat 400 proj.Rmd
print removed

@@
       new_status <- rbind(infected_people, other_people)
-      print(infected_people)
 

### 2021-12-07 Stat 400 proj.Rmd
Started creating a bootstrap function for each individual day

@@
 ```{r}
-
 #create starting positions and state function
@@
 new_status
-print(new_status[,4])
 
@@
 
-plot <- ggplot() +
+ggplot() +
   geom_line(aes(x=x, y=y)) +
@@
 #bootstrap
+mean_func <- function(daytuh, idx) {
+  mean(daytuh[idx])
+}
 
-mean_func <- function(x, idx) {
-  mean(x[idx])
+get_bootstrap_cis <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, sample_size, ci_type='perc'){
+  #Create data frame to store samples
+  samps <- matrix(data=NA, nrow=sample_size, ncol=days + 1)
+  samps <- data.frame(samps)
+
+  #Create data frame to store confidence intervals
+  ci_df <- matrix(data=NA, nrow=days + 1, ncol=2)
+  ci_df <- data.frame(ci_df)
+
+  for(i in 1:sample_size){
+    samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist)
   }
+
+  for(i in 1:ncol(samps)){
+    #Make sure column has more than one unique value
+    check <- (length(unique(samps[ ,i])) != 1)
+    if(check){
+    boot_obj <- boot(samps[ ,i], mean_func, 2000)
+    ci_obj <- boot.ci(boot_obj, conf = .95, type = ci_type)
+    ci_df[i, ] <- c(ci_obj$percent[4], ci_obj$percent[5])
+    }else{ci_df[i, ] <- c(samps[1, i], samps[1, i])}
+  }
+return(ci_df)
+}
+
+get_bootstrap_cis(days=50, num_subjects=100, x_dim=10, y_dim=10, I_0=2, inf_dist=1, sample_size=5)
 

### 2021-12-07 Stat 400 proj.Rmd
Got a bootstrap confidence interval graph

@@
   #Create data frame to store confidence intervals
-  ci_df <- matrix(data=NA, nrow=days + 1, ncol=2)
+  ci_df <- matrix(data=NA, nrow=days + 1, ncol=3)
   ci_df <- data.frame(ci_df)
@@
     ci_obj <- boot.ci(boot_obj, conf = .95, type = ci_type)
-    ci_df[i, ] <- c(ci_obj$percent[4], ci_obj$percent[5])
-    }else{ci_df[i, ] <- c(samps[1, i], samps[1, i])}
+    ci_df[i, 1] <- ci_obj$percent[4]
+    ci_df[i, 2] <- ci_obj$t0
+    ci_df[i, 3] <- ci_obj$percent[5]
+    }else{ci_df[i, ] <- c(samps[1, i], samps[1, i], samps[1, i])}
   }
@@
 
-get_bootstrap_cis(days=50, num_subjects=100, x_dim=10, y_dim=10, I_0=2, inf_dist=1, sample_size=5)
+plot_dat <- get_bootstrap_cis(days=50, num_subjects=100, x_dim=10, y_dim=10, I_0=2, inf_dist=1, sample_size=5)
+
+ggplot() +
+  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
+  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
+  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red')
 

### 2021-12-07 Stat 400 presentation.Rmd
Started Creating Slides

---
title: "Stat 400 Presentation"
authors: Nathan Hemenway, Mark Hinds, Ian Hall
date: "12/7/2021"
output:
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(width=200)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Starting Values Function

\tiny
```{r, echo=TRUE}
starting_vals <- function(num_subjects, I_0, x_dim, y_dim){

  #Infect I_0 many starting subjects
  subjects <- rep('S', num_subjects)
  infect <- sample(x = 1:num_subjects, size=I_0, replace=FALSE)
  subjects[infect] <- 'I'

  #Storage for x, y starting positions for the subjects
  start_x <- runif(n=num_subjects, min=0, max=x_dim)
  start_y <- runif(n=num_subjects, min=0, max=y_dim)

  inc_time <- rep(-1, num_subjects)
  rec_days <- rep(-1, num_subjects)

  #Put into a data frame
  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects, rec_days, inc_time))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  colnames(df)[3] <- 'subjects'
  colnames(df)[4] <- 'incubation'
  colnames(df)[5] <- 'recovery'

  #Assign a recovery time to the infected subjects
  df[df[,3] == 'I', 5] <- rpois(I_0, 14)

  #Assign an incubation time to the infected subjects
  df[df[,3] == 'I', 4] <- rpois(I_0, 5)

  return(df)
}
```

## Simulating Step Distance and Direction

\tiny
```{r, echo=TRUE}
get_step_length <- function(df, x_dim, y_dim){
  step_lengths <- rnorm(n=nrow(df), mean=min(x_dim, y_dim)/4, sd=min(x_dim, y_dim)/12)
  return(step_lengths)
}

get_step_direction <- function(length_vec){
  direction <- runif(n=length(length_vec), min=0, max=2*pi)
}

get_delts <- function(length_vec, direc_vec){
  delta_x <- length_vec * cos(direc_vec)
  delta_y <- length_vec * sin(direc_vec)
  return(cbind(delta_x, delta_y))
}
```

## Updating Coordinates and In-Bounds Check

\tiny
```{r, echo=TRUE}
update_coords <- function(og_df, delta_df){
  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=5)
  new_df <- data.frame(new_mx)
  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
  new_df[,3] <- og_df[,3]
  new_df[,4] <- og_df[,4]
  new_df[,5] <- og_df[,5]
  colnames(new_df) <- c('x', 'y', 'subjects', 'incubation', 'recovery')
  new_df
}

coord_checker <- function(og_df, new_df, x_dim, y_dim){
  baddies <- NULL
  for(i in 1:nrow(new_df)){
    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'x']) < 0 | as.numeric(new_df[i, 'y']) > y_dim | as.numeric(new_df[i, 'y']) < 0){
      baddies <- append(baddies, i)
    }
  }

  if(is.null(baddies)){
    return(new_df)
  }else{
  new_step <- get_step_length(new_df[i,], x_dim, y_dim)
  new_direction <- get_step_direction(new_step)
  new_change <- get_delts(new_step, new_direction)
  new_df <- update_coords(og_df[baddies,], new_change)
  full_df <- rbind(new_df, og_df[-baddies,])
  return(coord_checker(og_df, full_df, x_dim, y_dim))
  }
}
```

### 2021-12-07 Stat 400 proj.Rmd
Created a plot of the people's positions and infection status

@@
 ```
+
+```{r}
+simulator22 <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist){
+  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
+  end_day <- list()
+  num_cases <- rep(NA, days)
+  num_cases <- c(I_0, num_cases)
+  num_new_cases <- rep(NA, days)
+
+  for(i in 1:days){
+
+    if(i == 1){
+      step_size <- get_step_length(initial_data, x_dim, y_dim)
+      direction <- get_step_direction(step_size)
+      change <- get_delts(step_size, direction)
+
+      updated_positions <- update_coords(initial_data, change)
+      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
+      new_status <- infection_status(checked_positions, inf_dist)
+
+      #recovery time code
+      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
+      new_time <- as.numeric(not_recovered[, 5]) - 1
+      not_recovered[, 5] <- new_time
+      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
+      infected_0[, 3] <- rep('R', nrow(infected_0))
+      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
+      new_status = rbind(not_recovered, infected_0, not_infected)
+
+      #incubation time code
+      infected_people <- new_status[new_status[,3] == 'I',]
+      new_inc_time <- as.numeric(infected_people[,4]) - 1
+      infected_people[,4] <- new_inc_time
+      other_people <- new_status[new_status[,3] != 'I',]
+      new_status <- rbind(infected_people, other_people)
+
+      end_day[[i]] <- new_status
+
+      #Calculate number of new cases
+      num_cases[i+1] <- sum(new_status[,3]=='I')
+      num_new_cases[i] <- sum(new_status[,3]=='I') - I_0
+
+    }
+
+    else{
+      step_size <- get_step_length(initial_data, x_dim, y_dim)
+      direction <- get_step_direction(step_size)
+      change <- get_delts(step_size, direction)
+
+      updated_positions <- update_coords(end_day[[i-1]], change)
+      checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
+      new_status <- infection_status(checked_positions, inf_dist)
+
+      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
+      new_time <- as.numeric(not_recovered[, 5]) - 1
+      not_recovered[, 5] <- new_time
+      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
+      infected_0[, 3] <- rep('R', nrow(infected_0))
+      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
+      new_status = rbind(not_recovered, infected_0, not_infected)
+
+      #incubation time code
+      infected_people <- new_status[new_status[,3] == 'I',]
+      new_inc_time <- as.numeric(infected_people[,4]) - 1
+      infected_people[,4] <- new_inc_time
+      other_people <- new_status[new_status[,3] != 'I',]
+      new_status <- rbind(infected_people, other_people)
+
+      end_day[[i]] <- new_status
+
+      #Calculate number of new cases
+      num_cases[i+1] <- sum(new_status[,3]=='I')
+      num_new_cases[i] <- sum(new_status[,3]=='I') - num_cases[i-1]
+
+    }
+  }
+  return(end_day)
+}
+days <- simulator22(20, 5, 1, 1, 1, 0.2)
+days
+
+ggplot() +
+  geom_point(aes(x=days[[20]][, 'x'], y= days[[20]][, 'y'], color=days[[20]][, 'subjects']))
+```

### 2021-12-08 Stat 400 presentation.Rmd
Added in the plot, this code can probably be reduced

@@
 ```
+
+## Plot of infected people
+
+\tiny
+```{r, echo = FALSE, output = TRUE}
+library(ggplot2)
+starting_vals <- function(num_subjects, I_0, x_dim, y_dim){
+
+  #Infect I_0 many starting subjects
+  subjects <- rep('S', num_subjects)
+  infect <- sample(x = 1:num_subjects, size=I_0, replace=FALSE)
+  subjects[infect] <- 'I'
+
+  #Storage for x, y starting positions for the subjects
+  start_x <- runif(n=num_subjects, min=0, max=x_dim)
+  start_y <- runif(n=num_subjects, min=0, max=y_dim)
+
+  inc_time <- rep(-1, num_subjects)
+  rec_days <- rep(-1, num_subjects)
+
+  #Put into a data frame
+  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects, rec_days, inc_time))
+  colnames(df)[1] <- 'x'
+  colnames(df)[2] <- 'y'
+  colnames(df)[3] <- 'subjects'
+  colnames(df)[4] <- 'incubation'
+  colnames(df)[5] <- 'recovery'
+
+  #Assign a recovery time to the infected subjects
+  df[df[,3] == 'I', 5] <- rpois(I_0, 14)
+
+  #Assign an incubation time to the infected subjects
+  df[df[,3] == 'I', 4] <- rpois(I_0, 5)
+
+  return(df)
+}
+
+#Random step length function
+get_step_length <- function(df, x_dim, y_dim){
+  step_lengths <- rnorm(n=nrow(df), mean=min(x_dim, y_dim)/4, sd=min(x_dim, y_dim)/12)
+  return(step_lengths)
+}
+
+#Random step direction function
+get_step_direction <- function(length_vec){
+  direction <- runif(n=length(length_vec), min=0, max=2*pi)
+}
+
+#Get delta_x, delta_y
+get_delts <- function(length_vec, direc_vec){
+  delta_x <- length_vec * cos(direc_vec)
+  delta_y <- length_vec * sin(direc_vec)
+  return(cbind(delta_x, delta_y))
+}
+
+#Function for getting updated coordinates
+update_coords <- function(og_df, delta_df){
+  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=5)
+  new_df <- data.frame(new_mx)
+  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
+  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
+  new_df[,3] <- og_df[,3]
+  new_df[,4] <- og_df[,4]
+  new_df[,5] <- og_df[,5]
+  colnames(new_df) <- c('x', 'y', 'subjects', 'incubation', 'recovery')
+  new_df
+}
+
+coord_checker <- function(og_df, new_df, x_dim, y_dim){
+  baddies <- NULL
+  for(i in 1:nrow(new_df)){
+    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'x']) < 0 | as.numeric(new_df[i, 'y']) > y_dim | as.numeric(new_df[i, 'y']) < 0){
+      baddies <- append(baddies, i)
+    }
+  }
+
+  if(is.null(baddies)){
+    return(new_df)
+  }else{
+  new_step <- get_step_length(new_df[i,], x_dim, y_dim)
+  new_direction <- get_step_direction(new_step)
+  new_change <- get_delts(new_step, new_direction)
+  new_df <- update_coords(og_df[baddies,], new_change)
+  full_df <- rbind(new_df, og_df[-baddies,])
+  return(coord_checker(og_df, full_df, x_dim, y_dim))
+  }
+}
+
+#Function for deciding if infections occurred
+infection_status <- function(state, mean_crit_dist){
+
+  current_infected <- state[state[,3]=='I' & state[,4] <= 0,]
+  current_suceptable <- state[state[,3]=='S',]
+  current_removed <- state[state[,3]=='R',]
+  current_non_contagious <- state[state[,3]=='I' & state[,4] > 0,]
+
+  #store new infection status
+  newly_infected <- NULL
+
+  #Check to see which susceptible subjects get infected
+  #For loop
+  if(nrow(current_suceptable) != 0 & nrow(current_infected) != 0){
+  for(i in 1:nrow(current_infected)){
+    for(j in 1:nrow(current_suceptable)){
+      x_i <- as.numeric(current_infected[i, 'x'])
+      y_i <- as.numeric(current_infected[i, 'y'])
+      x_s <- as.numeric(current_suceptable[j, 'x'])
+      y_s <- as.numeric(current_suceptable[j, 'y'])
+
+      crucial_distance <- rexp(1, 1/mean_crit_dist)
+
+      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
+      if(d <= crucial_distance){
+        newly_infected <- c(newly_infected, j)
+      }
+
+    }
+  }
+
+  current_suceptable[newly_infected, 3] <- 'I'
+  #Give incubation time
+  current_suceptable[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5)
+  #Give recovery time
+  current_suceptable[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)
+
+  new_state <- rbind(current_infected, current_suceptable, current_removed, current_non_contagious)
+  return(new_state)
+  }else{return(state)}
+}
+
+#simulation function
+simulator <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist){
+  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
+  end_day <- list()
+  num_cases <- rep(NA, days)
+  num_cases <- c(I_0, num_cases)
+  num_new_cases <- rep(NA, days)
+
+  for(i in 1:days){
+
+    if(i == 1){
+      step_size <- get_step_length(initial_data, x_dim, y_dim)
+      direction <- get_step_direction(step_size)
+      change <- get_delts(step_size, direction)
+
+      updated_positions <- update_coords(initial_data, change)
+      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
+      new_status <- infection_status(checked_positions, inf_dist)
+
+      #recovery time code
+      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
+      new_time <- as.numeric(not_recovered[, 5]) - 1
+      not_recovered[, 5] <- new_time
+      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
+      infected_0[, 3] <- rep('R', nrow(infected_0))
+      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
+      new_status = rbind(not_recovered, infected_0, not_infected)
+
+      #incubation time code
+      infected_people <- new_status[new_status[,3] == 'I',]
+      new_inc_time <- as.numeric(infected_people[,4]) - 1
+      infected_people[,4] <- new_inc_time
+      other_people <- new_status[new_status[,3] != 'I',]
+      new_status <- rbind(infected_people, other_people)
+
+      end_day[[i]] <- new_status
+
+      #Calculate number of new cases
+      num_cases[i+1] <- sum(new_status[,3]=='I')
+      num_new_cases[i] <- sum(new_status[,3]=='I') - I_0
+
+    }
+
+    else{
+      step_size <- get_step_length(initial_data, x_dim, y_dim)
+      direction <- get_step_direction(step_size)
+      change <- get_delts(step_size, direction)
+
+      updated_positions <- update_coords(end_day[[i-1]], change)
+      checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
+      new_status <- infection_status(checked_positions, inf_dist)
+
+      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
+      new_time <- as.numeric(not_recovered[, 5]) - 1
+      not_recovered[, 5] <- new_time
+      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
+      infected_0[, 3] <- rep('R', nrow(infected_0))
+      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
+      new_status = rbind(not_recovered, infected_0, not_infected)
+
+      #incubation time code
+      infected_people <- new_status[new_status[,3] == 'I',]
+      new_inc_time <- as.numeric(infected_people[,4]) - 1
+      infected_people[,4] <- new_inc_time
+      other_people <- new_status[new_status[,3] != 'I',]
+      new_status <- rbind(infected_people, other_people)
+
+      end_day[[i]] <- new_status
+
+      #Calculate number of new cases
+      num_cases[i+1] <- sum(new_status[,3]=='I')
+      num_new_cases[i] <- sum(new_status[,3]=='I') - num_cases[i-1]
+
+    }
+  }
+  return(num_cases)
+}
+
+#Testing
+n=50
+y <- simulator(n,100,10,10,2,1)
+x <- 0:n
+
+ggplot() +
+  geom_line(aes(x=x, y=y)) +
+  xlab('Day') +
+  ylab('Number of Cases') +
+  ggtitle('Number of Covid-19 cases over time')
+```

### 2021-12-08 Stat 400 presentation.Rmd
Created a good demonstration of simulator

@@
 
-## R Markdown
+```{r}
+library(tidyverse)
+library(ggplot2)
+library(boot)
 
-This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-
-## Slide with Bullets
-
-- Bullet 1
-- Bullet 2
-- Bullet 3
-
-## Starting Values Function
-
-\tiny
-```{r, echo=TRUE}
-starting_vals <- function(num_subjects, I_0, x_dim, y_dim){
-
-  #Infect I_0 many starting subjects
-  subjects <- rep('S', num_subjects)
-  infect <- sample(x = 1:num_subjects, size=I_0, replace=FALSE)
-  subjects[infect] <- 'I'
-
-  #Storage for x, y starting positions for the subjects
-  start_x <- runif(n=num_subjects, min=0, max=x_dim)
-  start_y <- runif(n=num_subjects, min=0, max=y_dim)
-
-  inc_time <- rep(-1, num_subjects)
-  rec_days <- rep(-1, num_subjects)
-
-  #Put into a data frame
-  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects, rec_days, inc_time))
-  colnames(df)[1] <- 'x'
-  colnames(df)[2] <- 'y'
-  colnames(df)[3] <- 'subjects'
-  colnames(df)[4] <- 'incubation'
-  colnames(df)[5] <- 'recovery'
-
-  #Assign a recovery time to the infected subjects
-  df[df[,3] == 'I', 5] <- rpois(I_0, 14)
-
-  #Assign an incubation time to the infected subjects
-  df[df[,3] == 'I', 4] <- rpois(I_0, 5)
-
-  return(df)
-}
-```
-
-## Simulating Step Distance and Direction
-
-\tiny
-```{r, echo=TRUE}
-get_step_length <- function(df, x_dim, y_dim){
-  step_lengths <- rnorm(n=nrow(df), mean=min(x_dim, y_dim)/4, sd=min(x_dim, y_dim)/12)
-  return(step_lengths)
-}
-
-get_step_direction <- function(length_vec){
-  direction <- runif(n=length(length_vec), min=0, max=2*pi)
-}
-
-get_delts <- function(length_vec, direc_vec){
-  delta_x <- length_vec * cos(direc_vec)
-  delta_y <- length_vec * sin(direc_vec)
-  return(cbind(delta_x, delta_y))
-}
-```
-
-## Updating Coordinates and In-Bounds Check
-
-\tiny
-```{r, echo=TRUE}
-update_coords <- function(og_df, delta_df){
-  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=5)
-  new_df <- data.frame(new_mx)
-  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
-  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
-  new_df[,3] <- og_df[,3]
-  new_df[,4] <- og_df[,4]
-  new_df[,5] <- og_df[,5]
-  colnames(new_df) <- c('x', 'y', 'subjects', 'incubation', 'recovery')
-  new_df
-}
-
-coord_checker <- function(og_df, new_df, x_dim, y_dim){
-  baddies <- NULL
-  for(i in 1:nrow(new_df)){
-    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'x']) < 0 | as.numeric(new_df[i, 'y']) > y_dim | as.numeric(new_df[i, 'y']) < 0){
-      baddies <- append(baddies, i)
-    }
-  }
-
-  if(is.null(baddies)){
-    return(new_df)
-  }else{
-  new_step <- get_step_length(new_df[i,], x_dim, y_dim)
-  new_direction <- get_step_direction(new_step)
-  new_change <- get_delts(new_step, new_direction)
-  new_df <- update_coords(og_df[baddies,], new_change)
-  full_df <- rbind(new_df, og_df[-baddies,])
-  return(coord_checker(og_df, full_df, x_dim, y_dim))
-  }
-}
-```
-
-## Plot of infected people
-
-\tiny
-```{r, echo = FALSE, output = TRUE}
-library(ggplot2)
 starting_vals <- function(num_subjects, I_0, x_dim, y_dim){
@@
 
+simulator22 <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist){
+  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
+  end_day <- list()
+  num_cases <- rep(NA, days)
+  num_cases <- c(I_0, num_cases)
+  num_new_cases <- rep(NA, days)
+
+  for(i in 1:days){
+
+    if(i == 1){
+      step_size <- get_step_length(initial_data, x_dim, y_dim)
+      direction <- get_step_direction(step_size)
+      change <- get_delts(step_size, direction)
+
+      updated_positions <- update_coords(initial_data, change)
+      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
+      new_status <- infection_status(checked_positions, inf_dist)
+
+      #recovery time code
+      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
+      new_time <- as.numeric(not_recovered[, 5]) - 1
+      not_recovered[, 5] <- new_time
+      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
+      infected_0[, 3] <- rep('R', nrow(infected_0))
+      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
+      new_status = rbind(not_recovered, infected_0, not_infected)
+
+      #incubation time code
+      infected_people <- new_status[new_status[,3] == 'I',]
+      new_inc_time <- as.numeric(infected_people[,4]) - 1
+      infected_people[,4] <- new_inc_time
+      other_people <- new_status[new_status[,3] != 'I',]
+      new_status <- rbind(infected_people, other_people)
+
+      end_day[[i]] <- new_status
+
+      #Calculate number of new cases
+      num_cases[i+1] <- sum(new_status[,3]=='I')
+      num_new_cases[i] <- sum(new_status[,3]=='I') - I_0
+
+    }
+
+    else{
+      step_size <- get_step_length(initial_data, x_dim, y_dim)
+      direction <- get_step_direction(step_size)
+      change <- get_delts(step_size, direction)
+
+      updated_positions <- update_coords(end_day[[i-1]], change)
+      checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
+      new_status <- infection_status(checked_positions, inf_dist)
+
+      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
+      new_time <- as.numeric(not_recovered[, 5]) - 1
+      not_recovered[, 5] <- new_time
+      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
+      infected_0[, 3] <- rep('R', nrow(infected_0))
+      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
+      new_status = rbind(not_recovered, infected_0, not_infected)
+
+      #incubation time code
+      infected_people <- new_status[new_status[,3] == 'I',]
+      new_inc_time <- as.numeric(infected_people[,4]) - 1
+      infected_people[,4] <- new_inc_time
+      other_people <- new_status[new_status[,3] != 'I',]
+      new_status <- rbind(infected_people, other_people)
+
+      end_day[[i]] <- new_status
+
+      #Calculate number of new cases
+      num_cases[i+1] <- sum(new_status[,3]=='I')
+      num_new_cases[i] <- sum(new_status[,3]=='I') - num_cases[i-1]
+
+    }
+  }
+  return(end_day)
+}
+```
+
+## Simulating Step Distance and Direction
+
+\tiny
+```{r, echo=TRUE}
+get_step_length <- function(df, x_dim, y_dim){
+  step_lengths <- rnorm(n=nrow(df), mean=min(x_dim, y_dim)/4, sd=min(x_dim, y_dim)/12)
+  return(step_lengths)
+}
+
+get_step_direction <- function(length_vec){
+  direction <- runif(n=length(length_vec), min=0, max=2*pi)
+}
+
+get_delts <- function(length_vec, direc_vec){
+  delta_x <- length_vec * cos(direc_vec)
+  delta_y <- length_vec * sin(direc_vec)
+  return(cbind(delta_x, delta_y))
+}
+```
+
+## Updating Coordinates and In-Bounds Check
+
+\tiny
+```{r, echo=TRUE}
+update_coords <- function(og_df, delta_df){
+  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=5)
+  new_df <- data.frame(new_mx)
+  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
+  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
+  new_df[,3] <- og_df[,3]
+  new_df[,4] <- og_df[,4]
+  new_df[,5] <- og_df[,5]
+  colnames(new_df) <- c('x', 'y', 'subjects', 'incubation', 'recovery')
+  new_df
+}
+
+coord_checker <- function(og_df, new_df, x_dim, y_dim){
+  baddies <- NULL
+  for(i in 1:nrow(new_df)){
+    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'x']) < 0 | as.numeric(new_df[i, 'y']) > y_dim | as.numeric(new_df[i, 'y']) < 0){
+      baddies <- append(baddies, i)
+    }
+  }
+
+  if(is.null(baddies)){
+    return(new_df)
+  }else{
+  new_step <- get_step_length(new_df[i,], x_dim, y_dim)
+  new_direction <- get_step_direction(new_step)
+  new_change <- get_delts(new_step, new_direction)
+  new_df <- update_coords(og_df[baddies,], new_change)
+  full_df <- rbind(new_df, og_df[-baddies,])
+  return(coord_checker(og_df, full_df, x_dim, y_dim))
+  }
+}
+```
+
+## Changing SIR Status
+
+\tiny
+```{r, echo=TRUE}
+infection_status <- function(state, mean_crit_dist){
+
+  current_infected <- state[state[,3]=='I' & state[,4] <= 0,]
+  current_suceptable <- state[state[,3]=='S',]
+  current_removed <- state[state[,3]=='R',]
+  current_non_contagious <- state[state[,3]=='I' & state[,4] > 0,]
+
+  newly_infected <- NULL
+
+  if(nrow(current_suceptable) != 0 & nrow(current_infected) != 0){
+  for(i in 1:nrow(current_infected)){
+    for(j in 1:nrow(current_suceptable)){
+      x_i <- as.numeric(current_infected[i, 'x'])
+      y_i <- as.numeric(current_infected[i, 'y'])
+      x_s <- as.numeric(current_suceptable[j, 'x'])
+      y_s <- as.numeric(current_suceptable[j, 'y'])
+
+      crucial_distance <- rexp(1, 1/mean_crit_dist)
+
+      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
+      if(d <= crucial_distance){
+        newly_infected <- c(newly_infected, j)
+      }
+    }
+  }
+  current_suceptable[newly_infected, 3] <- 'I'
+  current_suceptable[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5)
+  current_suceptable[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)
+
+  new_state <- rbind(current_infected, current_suceptable, current_removed, current_non_contagious)
+  return(new_state)
+  }else{return(state)}
+}
+```
+
+## Simulation
+
+\tiny
+```{r, echo=TRUE}
+dummy_simulator <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist){
+  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
+  end_day <- list()
+  num_cases <- rep(NA, days)
+  num_cases <- c(I_0, num_cases)
+  num_new_cases <- rep(NA, days)
+  for(i in 1:days){
+    if(i == 1){
+      step_size <- get_step_length(initial_data, x_dim, y_dim)
+      direction <- get_step_direction(step_size)
+      change <- get_delts(step_size, direction)
+      updated_positions <- update_coords(initial_data, change)
+      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
+      new_status <- infection_status(checked_positions, inf_dist)
+
+      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
+      new_time <- as.numeric(not_recovered[, 5]) - 1
+      not_recovered[, 5] <- new_time
+      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
+      infected_0[, 3] <- rep('R', nrow(infected_0))
+      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
+      new_status = rbind(not_recovered, infected_0, not_infected)
+      infected_people <- new_status[new_status[,3] == 'I',]
+      new_inc_time <- as.numeric(infected_people[,4]) - 1
+      infected_people[,4] <- new_inc_time
+      other_people <- new_status[new_status[,3] != 'I',]
+      new_status <- rbind(infected_people, other_people)
+      end_day[[i]] <- new_status
+      num_cases[i+1] <- sum(new_status[,3]=='I')
+      num_new_cases[i] <- sum(new_status[,3]=='I') - I_0
+    }
+    }
+  return(num_cases)
+}
+```
+
+## Demonstration Day 1
+
+```{r}
+days <- simulator22(30, 10, 1, 1, 1, 0.2)
+
+ggplot() +
+  geom_point(aes(x=days[[1]][, 'x'], y= days[[1]][, 'y'], color=days[[1]][, 'subjects'])) +
+  xlab('x position') +
+  ylab('y position') +
+  ggtitle('Infection Status and Position') +
+  theme(axis.text.x=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.y=element_blank(),
+        axis.ticks.y=element_blank())
+
+```
+
+## Demonstration Day 5
+
+```{r}
+ggplot() +
+  geom_point(aes(x=days[[5]][, 'x'], y= days[[5]][, 'y'], color=days[[5]][, 'subjects'])) +
+  xlab('x position') +
+  ylab('y position') +
+  ggtitle('Infection Status and Position') +
+  theme(axis.text.x=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.y=element_blank(),
+        axis.ticks.y=element_blank())
+
+```
+
+## Demonstration Day 10
+
+```{r}
+ggplot() +
+  geom_point(aes(x=days[[10]][, 'x'], y= days[[10]][, 'y'], color=days[[10]][, 'subjects'])) +
+  xlab('x position') +
+  ylab('y position') +
+  ggtitle('Infection Status and Position') +
+  theme(axis.text.x=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.y=element_blank(),
+        axis.ticks.y=element_blank())
+
+```
+
+## Demonstration Day 15
+
+```{r}
+ggplot() +
+  geom_point(aes(x=days[[15]][, 'x'], y= days[[15]][, 'y'], color=days[[15]][, 'subjects'])) +
+  xlab('x position') +
+  ylab('y position') +
+  ggtitle('Infection Status and Position') +
+  theme(axis.text.x=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.y=element_blank(),
+        axis.ticks.y=element_blank())
+
+```
+
+## Demonstration Day 20
+
+```{r}
+ggplot() +
+  geom_point(aes(x=days[[20]][, 'x'], y= days[[20]][, 'y'], color=days[[20]][, 'subjects'])) +
+  xlab('x position') +
+  ylab('y position') +
+  ggtitle('Infection Status and Position') +
+  theme(axis.text.x=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.y=element_blank(),
+        axis.ticks.y=element_blank())
+
+```
+
+## Demonstration Day 25
+
+```{r}
+ggplot() +
+  geom_point(aes(x=days[[25]][, 'x'], y= days[[25]][, 'y'], color=days[[25]][, 'subjects'])) +
+  xlab('x position') +
+  ylab('y position') +
+  ggtitle('Infection Status and Position') +
+  theme(axis.text.x=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.y=element_blank(),
+        axis.ticks.y=element_blank())
+
+```
+
+## Demonstration Day 30
+
+```{r}
+ggplot() +
+  geom_point(aes(x=days[[30]][, 'x'], y= days[[30]][, 'y'], color=days[[30]][, 'subjects'])) +
+  xlab('x position') +
+  ylab('y position') +
+  ggtitle('Infection Status and Position') +
+  theme(axis.text.x=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.y=element_blank(),
+        axis.ticks.y=element_blank())
+
+```
+
+## Bootstrap Confidence Intervals
+
+\tiny
+```{r, echo=TRUE}
+get_bootstrap_cis <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, sample_size, ci_type='perc'){
+  #Create data frame to store samples
+  samps <- matrix(data=NA, nrow=sample_size, ncol=days + 1)
+  samps <- data.frame(samps)
+
+  #Create data frame to store confidence intervals
+  ci_df <- matrix(data=NA, nrow=days + 1, ncol=3)
+  ci_df <- data.frame(ci_df)
+
+  for(i in 1:sample_size){
+    samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist)
+  }
+
+  for(i in 1:ncol(samps)){
+    #Make sure column has more than one unique value
+    check <- (length(unique(samps[ ,i])) != 1)
+    if(check){
+    boot_obj <- boot(samps[ ,i], mean_func, 2000)
+    ci_obj <- boot.ci(boot_obj, conf = .95, type = ci_type)
+    ci_df[i, 1] <- ci_obj$percent[4]
+    ci_df[i, 2] <- ci_obj$t0
+    ci_df[i, 3] <- ci_obj$percent[5]
+    }else{ci_df[i, ] <- c(samps[1, i], samps[1, i], samps[1, i])}
+  }
+return(ci_df)
+}
+```
+
+## Plot of infected people
+
+\tiny
+```{r, echo = FALSE, output = TRUE}
+library(ggplot2)
+
 #Testing
@@
 x <- 0:n
+
+y
 
@@
   ggtitle('Number of Covid-19 cases over time')
+
 ```

### 2021-12-08 Stat 400 presentation.Rmd
Added bootstrap

--- 2021-12-08 Stat 400 presentation.Rmd
@@
 
-## Plot of infected people
+## Plot of infected people with bootstrap
 
@@
 library(ggplot2)
+library(boot)
 starting_vals <- function(num_subjects, I_0, x_dim, y_dim){
@@
 
+#bootstrap
+mean_func <- function(daytuh, idx) {
+  mean(daytuh[idx])
+}
+
+get_bootstrap_cis <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, sample_size, ci_type='perc'){
+  #Create data frame to store samples
+  samps <- matrix(data=NA, nrow=sample_size, ncol=days + 1)
+  samps <- data.frame(samps)
+
+  #Create data frame to store confidence intervals
+  ci_df <- matrix(data=NA, nrow=days + 1, ncol=3)
+  ci_df <- data.frame(ci_df)
+
+  for(i in 1:sample_size){
+    samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist)
+  }
+
+  for(i in 1:ncol(samps)){
+    #Make sure column has more than one unique value
+    check <- (length(unique(samps[ ,i])) != 1)
+    if(check){
+    boot_obj <- boot(samps[ ,i], mean_func, 2000)
+    ci_obj <- boot.ci(boot_obj, conf = .95, type = ci_type)
+    ci_df[i, 1] <- ci_obj$percent[4]
+    ci_df[i, 2] <- ci_obj$t0
+    ci_df[i, 3] <- ci_obj$percent[5]
+    }else{ci_df[i, ] <- c(samps[1, i], samps[1, i], samps[1, i])}
+  }
+return(ci_df)
+}
+
+plot_dat <- get_bootstrap_cis(days=50, num_subjects=100, x_dim=10, y_dim=10, I_0=2, inf_dist=1, sample_size=5)
+
 ggplot() +
-  geom_line(aes(x=x, y=y)) +
+  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
+  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
+  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red') +
   xlab('Day') +
@@
 ```
+
+## Boostrap
+
+```{r, echo = F}
+library(boot)
+starting_vals <- function(num_subjects, I_0, x_dim, y_dim){
+
+  #Infect I_0 many starting subjects
+  subjects <- rep('S', num_subjects)
+  infect <- sample(x = 1:num_subjects, size=I_0, replace=FALSE)
+  subjects[infect] <- 'I'
+
+  #Storage for x, y starting positions for the subjects
+  start_x <- runif(n=num_subjects, min=0, max=x_dim)
+  start_y <- runif(n=num_subjects, min=0, max=y_dim)
+
+  inc_time <- rep(-1, num_subjects)
+  rec_days <- rep(-1, num_subjects)
+
+  #Put into a data frame
+  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects, rec_days, inc_time))
+  colnames(df)[1] <- 'x'
+  colnames(df)[2] <- 'y'
+  colnames(df)[3] <- 'subjects'
+  colnames(df)[4] <- 'incubation'
+  colnames(df)[5] <- 'recovery'
+
+  #Assign a recovery time to the infected subjects
+  df[df[,3] == 'I', 5] <- rpois(I_0, 14)
+
+  #Assign an incubation time to the infected subjects
+  df[df[,3] == 'I', 4] <- rpois(I_0, 5)
+
+  return(df)
+}
+
+#Random step length function
+get_step_length <- function(df, x_dim, y_dim){
+  step_lengths <- rnorm(n=nrow(df), mean=min(x_dim, y_dim)/4, sd=min(x_dim, y_dim)/12)
+  return(step_lengths)
+}
+
+#Random step direction function
+get_step_direction <- function(length_vec){
+  direction <- runif(n=length(length_vec), min=0, max=2*pi)
+}
+
+#Get delta_x, delta_y
+get_delts <- function(length_vec, direc_vec){
+  delta_x <- length_vec * cos(direc_vec)
+  delta_y <- length_vec * sin(direc_vec)
+  return(cbind(delta_x, delta_y))
+}
+
+#Function for getting updated coordinates
+update_coords <- function(og_df, delta_df){
+  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=5)
+  new_df <- data.frame(new_mx)
+  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
+  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
+  new_df[,3] <- og_df[,3]
+  new_df[,4] <- og_df[,4]
+  new_df[,5] <- og_df[,5]
+  colnames(new_df) <- c('x', 'y', 'subjects', 'incubation', 'recovery')
+  new_df
+}
+
+coord_checker <- function(og_df, new_df, x_dim, y_dim){
+  baddies <- NULL
+  for(i in 1:nrow(new_df)){
+    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'x']) < 0 | as.numeric(new_df[i, 'y']) > y_dim | as.numeric(new_df[i, 'y']) < 0){
+      baddies <- append(baddies, i)
+    }
+  }
+
+  if(is.null(baddies)){
+    return(new_df)
+  }else{
+  new_step <- get_step_length(new_df[i,], x_dim, y_dim)
+  new_direction <- get_step_direction(new_step)
+  new_change <- get_delts(new_step, new_direction)
+  new_df <- update_coords(og_df[baddies,], new_change)
+  full_df <- rbind(new_df, og_df[-baddies,])
+  return(coord_checker(og_df, full_df, x_dim, y_dim))
+  }
+}
+
+#Function for deciding if infections occurred
+infection_status <- function(state, mean_crit_dist){
+
+  current_infected <- state[state[,3]=='I' & state[,4] <= 0,]
+  current_suceptable <- state[state[,3]=='S',]
+  current_removed <- state[state[,3]=='R',]
+  current_non_contagious <- state[state[,3]=='I' & state[,4] > 0,]
+
+  #store new infection status
+  newly_infected <- NULL
+
+  #Check to see which susceptible subjects get infected
+  #For loop
+  if(nrow(current_suceptable) != 0 & nrow(current_infected) != 0){
+  for(i in 1:nrow(current_infected)){
+    for(j in 1:nrow(current_suceptable)){
+      x_i <- as.numeric(current_infected[i, 'x'])
+      y_i <- as.numeric(current_infected[i, 'y'])
+      x_s <- as.numeric(current_suceptable[j, 'x'])
+      y_s <- as.numeric(current_suceptable[j, 'y'])
+
+      crucial_distance <- rexp(1, 1/mean_crit_dist)
+
+      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
+      if(d <= crucial_distance){
+        newly_infected <- c(newly_infected, j)
+      }
+
+    }
+  }
+
+  current_suceptable[newly_infected, 3] <- 'I'
+  #Give incubation time
+  current_suceptable[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5)
+  #Give recovery time
+  current_suceptable[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)
+
+  new_state <- rbind(current_infected, current_suceptable, current_removed, current_non_contagious)
+  return(new_state)
+  }else{return(state)}
+}
+
+#simulation function
+simulator <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist){
+  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
+  end_day <- list()
+  num_cases <- rep(NA, days)
+  num_cases <- c(I_0, num_cases)
+  num_new_cases <- rep(NA, days)
+
+  for(i in 1:days){
+
+    if(i == 1){
+      step_size <- get_step_length(initial_data, x_dim, y_dim)
+      direction <- get_step_direction(step_size)
+      change <- get_delts(step_size, direction)
+
+      updated_positions <- update_coords(initial_data, change)
+      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
+      new_status <- infection_status(checked_positions, inf_dist)
+
+      #recovery time code
+      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
+      new_time <- as.numeric(not_recovered[, 5]) - 1
+      not_recovered[, 5] <- new_time
+      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
+      infected_0[, 3] <- rep('R', nrow(infected_0))
+      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
+      new_status = rbind(not_recovered, infected_0, not_infected)
+
+      #incubation time code
+      infected_people <- new_status[new_status[,3] == 'I',]
+      new_inc_time <- as.numeric(infected_people[,4]) - 1
+      infected_people[,4] <- new_inc_time
+      other_people <- new_status[new_status[,3] != 'I',]
+      new_status <- rbind(infected_people, other_people)
+
+      end_day[[i]] <- new_status
+
+      #Calculate number of new cases
+      num_cases[i+1] <- sum(new_status[,3]=='I')
+      num_new_cases[i] <- sum(new_status[,3]=='I') - I_0
+
+    }
+
+    else{
+      step_size <- get_step_length(initial_data, x_dim, y_dim)
+      direction <- get_step_direction(step_size)
+      change <- get_delts(step_size, direction)
+
+      updated_positions <- update_coords(end_day[[i-1]], change)
+      checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
+      new_status <- infection_status(checked_positions, inf_dist)
+
+      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
+      new_time <- as.numeric(not_recovered[, 5]) - 1
+      not_recovered[, 5] <- new_time
+      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
+      infected_0[, 3] <- rep('R', nrow(infected_0))
+      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
+      new_status = rbind(not_recovered, infected_0, not_infected)
+
+      #incubation time code
+      infected_people <- new_status[new_status[,3] == 'I',]
+      new_inc_time <- as.numeric(infected_people[,4]) - 1
+      infected_people[,4] <- new_inc_time
+      other_people <- new_status[new_status[,3] != 'I',]
+      new_status <- rbind(infected_people, other_people)
+
+      end_day[[i]] <- new_status
+
+      #Calculate number of new cases
+      num_cases[i+1] <- sum(new_status[,3]=='I')
+      num_new_cases[i] <- sum(new_status[,3]=='I') - num_cases[i-1]
+
+    }
+  }
+  return(num_cases)
+}
+
+#Testing
+df <- starting_vals(1000, 2, 1, 1)
+len <- get_step_length(df, 1, 1)
+dir <- get_step_direction(len)
+delts <- get_delts(len, dir)
+newdf <- update_coords(df, delts)
+coords <- coord_checker(df, newdf, 1, 1)
+new_status <- infection_status(coords, 8)
+
+set.seed(400)
+n=50
+y <- simulator(n,100,10,10,2,1)
+x <- 0:n
+
+#bootstrap
+mean_func <- function(daytuh, idx) {
+  mean(daytuh[idx])
+}
+
+get_bootstrap_cis <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, sample_size, ci_type='perc'){
+  #Create data frame to store samples
+  samps <- matrix(data=NA, nrow=sample_size, ncol=days + 1)
+  samps <- data.frame(samps)
+
+  #Create data frame to store confidence intervals
+  ci_df <- matrix(data=NA, nrow=days + 1, ncol=3)
+  ci_df <- data.frame(ci_df)
+
+  for(i in 1:sample_size){
+    samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist)
+  }
+
+  for(i in 1:ncol(samps)){
+    #Make sure column has more than one unique value
+    check <- (length(unique(samps[ ,i])) != 1)
+    if(check){
+    boot_obj <- boot(samps[ ,i], mean_func, 2000)
+    ci_obj <- boot.ci(boot_obj, conf = .95, type = ci_type)
+    ci_df[i, 1] <- ci_obj$percent[4]
+    ci_df[i, 2] <- ci_obj$t0
+    ci_df[i, 3] <- ci_obj$percent[5]
+    }else{ci_df[i, ] <- c(samps[1, i], samps[1, i], samps[1, i])}
+  }
+return(ci_df)
+}
+
+plot_dat <- get_bootstrap_cis(days=50, num_subjects=100, x_dim=10, y_dim=10, I_0=2, inf_dist=1, sample_size=5)
+
+daily_cases <- y
+boot.case <- boot(daily_cases, mean_func, 2000)
+
+plot(boot.case)
+
+```

### 2021-12-08 Stat 400 presentation.Rmd
Intro slides (mostly complete)

--- 2021-12-08 Stat 400 presentation.Rmd
@@
 
+## Novel approach for Monte Carlo simulation of the new COVID-19 spread dynamics
+
+Original Authors: Stavros Maltezos, Angelika Georgapakopoulou
+
+Resimulated by: Nathan Hemenway, Mark Hinds, Ian Hall
+
+## Introduction
+
+- Aim to investigate the transmission and incubation random processes of COVID-19.
+
+- Our focus will be on simulating daily infection case counts.
+
+- The goal of the study is to generate epidemiological based on natural mechanism of transmission of this disease assuming random interactions of a large-finite number of individuals in very short distance ranges.
+
+## Assumptions
+
+- The transmission of the virus occurs when the physical distance between individuals decreases to where the probability of transmission converges to one, asymptotmically.
+
+- the step of movement of people is a randomly assigned process.
+
+- the specific parameters of focus will be recovery and incubation time.
+
+##
+
+## General Model
+
+- Step Function
+    - Consider dots on a plane, with random
+
+- This is approached through an SIR model: Susceptible, Infected, Recovered. All change based on time.
+
+## Variables
+
+- not complete
+
 ## Simulating Step Distance and Direction

### 2021-12-08 Stat 400 presentation.Rmd
It was being buggy with the merge. I tried to fix it to how I believe you guys wanted it. Add or move anything that you feel is out of order. Also right now the pdf has a blank page for the second slide.

--- 2021-12-08 Stat 400 presentation.Rmd
@@
 library(tidyverse)
+library(ggplot2)
+library(boot)
+```
+
+## Plot of infected people with bootstrap
+
+\tiny
+```{r, echo = FALSE, output = TRUE}
 library(ggplot2)
@@
 
-## Plot of infected people
+## Boostrap plot of infected people
 
@@
 
-y
+#bootstrap
+mean_func <- function(daytuh, idx) {
+  mean(daytuh[idx])
+}
+
+get_bootstrap_cis <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, sample_size, ci_type='perc'){
+  #Create data frame to store samples
+  samps <- matrix(data=NA, nrow=sample_size, ncol=days + 1)
+  samps <- data.frame(samps)
+
+  #Create data frame to store confidence intervals
+  ci_df <- matrix(data=NA, nrow=days + 1, ncol=3)
+  ci_df <- data.frame(ci_df)
+
+  for(i in 1:sample_size){
+    samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist)
+  }
+
+  for(i in 1:ncol(samps)){
+    #Make sure column has more than one unique value
+    check <- (length(unique(samps[ ,i])) != 1)
+    if(check){
+    boot_obj <- boot(samps[ ,i], mean_func, 2000)
+    ci_obj <- boot.ci(boot_obj, conf = .95, type = ci_type)
+    ci_df[i, 1] <- ci_obj$percent[4]
+    ci_df[i, 2] <- ci_obj$t0
+    ci_df[i, 3] <- ci_obj$percent[5]
+    }else{ci_df[i, ] <- c(samps[1, i], samps[1, i], samps[1, i])}
+  }
+return(ci_df)
+}
+
+plot_dat <- get_bootstrap_cis(days=50, num_subjects=100, x_dim=10, y_dim=10, I_0=2, inf_dist=1, sample_size=5)
 
 ggplot() +
-  geom_line(aes(x=x, y=y)) +
+  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
+  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
+  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red') +
   xlab('Day') +
@@
   ggtitle('Number of Covid-19 cases over time')
+```
+
+## Boostrap
+
+```{r, echo = F}
+library(boot)
+starting_vals <- function(num_subjects, I_0, x_dim, y_dim){
+
+  #Infect I_0 many starting subjects
+  subjects <- rep('S', num_subjects)
+  infect <- sample(x = 1:num_subjects, size=I_0, replace=FALSE)
+  subjects[infect] <- 'I'
+
+  #Storage for x, y starting positions for the subjects
+  start_x <- runif(n=num_subjects, min=0, max=x_dim)
+  start_y <- runif(n=num_subjects, min=0, max=y_dim)
+
+  inc_time <- rep(-1, num_subjects)
+  rec_days <- rep(-1, num_subjects)
+
+  #Put into a data frame
+  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects, rec_days, inc_time))
+  colnames(df)[1] <- 'x'
+  colnames(df)[2] <- 'y'
+  colnames(df)[3] <- 'subjects'
+  colnames(df)[4] <- 'incubation'
+  colnames(df)[5] <- 'recovery'
+
+  #Assign a recovery time to the infected subjects
+  df[df[,3] == 'I', 5] <- rpois(I_0, 14)
+
+  #Assign an incubation time to the infected subjects
+  df[df[,3] == 'I', 4] <- rpois(I_0, 5)
+
+  return(df)
+}
+
+#Random step length function
+get_step_length <- function(df, x_dim, y_dim){
+  step_lengths <- rnorm(n=nrow(df), mean=min(x_dim, y_dim)/4, sd=min(x_dim, y_dim)/12)
+  return(step_lengths)
+}
+
+#Random step direction function
+get_step_direction <- function(length_vec){
+  direction <- runif(n=length(length_vec), min=0, max=2*pi)
+}
+
+#Get delta_x, delta_y
+get_delts <- function(length_vec, direc_vec){
+  delta_x <- length_vec * cos(direc_vec)
+  delta_y <- length_vec * sin(direc_vec)
+  return(cbind(delta_x, delta_y))
+}
+
+#Function for getting updated coordinates
+update_coords <- function(og_df, delta_df){
+  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=5)
+  new_df <- data.frame(new_mx)
+  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
+  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
+  new_df[,3] <- og_df[,3]
+  new_df[,4] <- og_df[,4]
+  new_df[,5] <- og_df[,5]
+  colnames(new_df) <- c('x', 'y', 'subjects', 'incubation', 'recovery')
+  new_df
+}
+
+coord_checker <- function(og_df, new_df, x_dim, y_dim){
+  baddies <- NULL
+  for(i in 1:nrow(new_df)){
+    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'x']) < 0 | as.numeric(new_df[i, 'y']) > y_dim | as.numeric(new_df[i, 'y']) < 0){
+      baddies <- append(baddies, i)
+    }
+  }
+
+  if(is.null(baddies)){
+    return(new_df)
+  }else{
+  new_step <- get_step_length(new_df[i,], x_dim, y_dim)
+  new_direction <- get_step_direction(new_step)
+  new_change <- get_delts(new_step, new_direction)
+  new_df <- update_coords(og_df[baddies,], new_change)
+  full_df <- rbind(new_df, og_df[-baddies,])
+  return(coord_checker(og_df, full_df, x_dim, y_dim))
+  }
+}
+
+#Function for deciding if infections occurred
+infection_status <- function(state, mean_crit_dist){
+
+  current_infected <- state[state[,3]=='I' & state[,4] <= 0,]
+  current_suceptable <- state[state[,3]=='S',]
+  current_removed <- state[state[,3]=='R',]
+  current_non_contagious <- state[state[,3]=='I' & state[,4] > 0,]
+
+  #store new infection status
+  newly_infected <- NULL
+
+  #Check to see which susceptible subjects get infected
+  #For loop
+  if(nrow(current_suceptable) != 0 & nrow(current_infected) != 0){
+  for(i in 1:nrow(current_infected)){
+    for(j in 1:nrow(current_suceptable)){
+      x_i <- as.numeric(current_infected[i, 'x'])
+      y_i <- as.numeric(current_infected[i, 'y'])
+      x_s <- as.numeric(current_suceptable[j, 'x'])
+      y_s <- as.numeric(current_suceptable[j, 'y'])
+
+      crucial_distance <- rexp(1, 1/mean_crit_dist)
+
+      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
+      if(d <= crucial_distance){
+        newly_infected <- c(newly_infected, j)
+      }
+
+    }
+  }
+
+  current_suceptable[newly_infected, 3] <- 'I'
+  #Give incubation time
+  current_suceptable[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5)
+  #Give recovery time
+  current_suceptable[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)
+
+  new_state <- rbind(current_infected, current_suceptable, current_removed, current_non_contagious)
+  return(new_state)
+  }else{return(state)}
+}
+
+#simulation function
+simulator <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist){
+  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
+  end_day <- list()
+  num_cases <- rep(NA, days)
+  num_cases <- c(I_0, num_cases)
+  num_new_cases <- rep(NA, days)
+
+  for(i in 1:days){
+
+    if(i == 1){
+      step_size <- get_step_length(initial_data, x_dim, y_dim)
+      direction <- get_step_direction(step_size)
+      change <- get_delts(step_size, direction)
+
+      updated_positions <- update_coords(initial_data, change)
+      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
+      new_status <- infection_status(checked_positions, inf_dist)
+
+      #recovery time code
+      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
+      new_time <- as.numeric(not_recovered[, 5]) - 1
+      not_recovered[, 5] <- new_time
+      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
+      infected_0[, 3] <- rep('R', nrow(infected_0))
+      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
+      new_status = rbind(not_recovered, infected_0, not_infected)
+
+      #incubation time code
+      infected_people <- new_status[new_status[,3] == 'I',]
+      new_inc_time <- as.numeric(infected_people[,4]) - 1
+      infected_people[,4] <- new_inc_time
+      other_people <- new_status[new_status[,3] != 'I',]
+      new_status <- rbind(infected_people, other_people)
+
+      end_day[[i]] <- new_status
+
+      #Calculate number of new cases
+      num_cases[i+1] <- sum(new_status[,3]=='I')
+      num_new_cases[i] <- sum(new_status[,3]=='I') - I_0
+
+    }
+
+    else{
+      step_size <- get_step_length(initial_data, x_dim, y_dim)
+      direction <- get_step_direction(step_size)
+      change <- get_delts(step_size, direction)
+
+      updated_positions <- update_coords(end_day[[i-1]], change)
+      checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
+      new_status <- infection_status(checked_positions, inf_dist)
+
+      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
+      new_time <- as.numeric(not_recovered[, 5]) - 1
+      not_recovered[, 5] <- new_time
+      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
+      infected_0[, 3] <- rep('R', nrow(infected_0))
+      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
+      new_status = rbind(not_recovered, infected_0, not_infected)
+
+      #incubation time code
+      infected_people <- new_status[new_status[,3] == 'I',]
+      new_inc_time <- as.numeric(infected_people[,4]) - 1
+      infected_people[,4] <- new_inc_time
+      other_people <- new_status[new_status[,3] != 'I',]
+      new_status <- rbind(infected_people, other_people)
+
+      end_day[[i]] <- new_status
+
+      #Calculate number of new cases
+      num_cases[i+1] <- sum(new_status[,3]=='I')
+      num_new_cases[i] <- sum(new_status[,3]=='I') - num_cases[i-1]
+
+    }
+  }
+  return(num_cases)
+}
+
+#Testing
+df <- starting_vals(1000, 2, 1, 1)
+len <- get_step_length(df, 1, 1)
+dir <- get_step_direction(len)
+delts <- get_delts(len, dir)
+newdf <- update_coords(df, delts)
+coords <- coord_checker(df, newdf, 1, 1)
+new_status <- infection_status(coords, 8)
+
+set.seed(400)
+n=50
+y <- simulator(n,100,10,10,2,1)
+x <- 0:n
+
+#bootstrap
+mean_func <- function(daytuh, idx) {
+  mean(daytuh[idx])
+}
+
+get_bootstrap_cis <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, sample_size, ci_type='perc'){
+  #Create data frame to store samples
+  samps <- matrix(data=NA, nrow=sample_size, ncol=days + 1)
+  samps <- data.frame(samps)
+
+  #Create data frame to store confidence intervals
+  ci_df <- matrix(data=NA, nrow=days + 1, ncol=3)
+  ci_df <- data.frame(ci_df)
+
+  for(i in 1:sample_size){
+    samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist)
+  }
+
+  for(i in 1:ncol(samps)){
+    #Make sure column has more than one unique value
+    check <- (length(unique(samps[ ,i])) != 1)
+    if(check){
+    boot_obj <- boot(samps[ ,i], mean_func, 2000)
+    ci_obj <- boot.ci(boot_obj, conf = .95, type = ci_type)
+    ci_df[i, 1] <- ci_obj$percent[4]
+    ci_df[i, 2] <- ci_obj$t0
+    ci_df[i, 3] <- ci_obj$percent[5]
+    }else{ci_df[i, ] <- c(samps[1, i], samps[1, i], samps[1, i])}
+  }
+return(ci_df)
+}
+
+plot_dat <- get_bootstrap_cis(days=50, num_subjects=100, x_dim=10, y_dim=10, I_0=2, inf_dist=1, sample_size=5)
+
+daily_cases <- y
+boot.case <- boot(daily_cases, mean_func, 2000)
+
+plot(boot.case)
 

### 2021-12-08 Stat 400 presentation.Rmd

@@
 ```{r, echo = FALSE, output = TRUE}
-library(ggplot2)
-library(boot)
 
@@
 ```
+
+## Novel approach for Monte Carlo simulation of the new COVID-19 spread dynamics
+
+Original Authors: Stavros Maltezos, Angelika Georgapakopoulou
+
+Resimulated by: Nathan Hemenway, Mark Hinds, Ian Hall
+
+## Introduction
+
+- Aim to investigate the transmission and incubation random processes of COVID-19.
+
+- Our focus will be on simulating daily infection case counts.
+
+- The goal of the study is to generate epidemiological based on natural mechanism of transmission of this disease assuming random interactions of a large-finite number of individuals in very short distance ranges.
+
+## Assumptions
+
+- The transmission of the virus occurs when the physical distance between individuals decreases to where the probability of transmission converges to one, asymptotmically.
+
+- the step of movement of people is a randomly assigned process.
+
+- the specific parameters of focus will be recovery and incubation time.
+
+##
+
+## General Model
+
+- Step Function
+    - Consider dots on a plane, with random
+
+- This is approached through an SIR model: Susceptible, Infected, Recovered. All change based on time.
+
+## Variables
+
+- not complete
 

### 2021-12-08 Stat 400 presentation.Rmd
finished intro slides + image

@@
 
-##
-
 ## General Model
@@
 - Step Function
-    - Consider dots on a plane, with random
+  ![Sample](/cloud/project/image.jpg)
 
-- This is approached through an SIR model: Susceptible, Infected, Recovered. All change based on time.
+- This is approached through an SIR model: Susceptible, Infected, Recovered. All change based on time as the function iterates through a set number of days. 
+  - 0.5% of the initial subjects start out with the virus (infected)
+  - 99.5% subjects are susceptible
+  - 0% recovered
 
@@
 
-- not complete
+- Factors to consider in the transmission of a virus. 
+  - What is the relationship and distribution between the infection probability and the physical distance
+  - High/low virus load, varying physical distances, ineffective vs effective mask wearing. 
+  - Environmental conditions: humidity, temperature, air ventilation. 
+- Based on real epidemiological data analysis, these encompassing factors will be distributed Exponential(rate = lambda)
+- Recovery and Incubation times ~ Gamma(alpha, beta), But in order to get whole number for days, we distribute them Possion(lambda)
 

### 2021-12-08 Stat 400 presentation.Rmd
Added new graphs and cleaned up a bit

@@
 
-```{r}
+```{r,include=FALSE}
 library(tidyverse)
@@
 
-## Plot of infected people with bootstrap
-
-\tiny
-```{r, echo = FALSE, output = TRUE}
-
+```{r, echo=FALSE, results='hide'}
 starting_vals <- function(num_subjects, I_0, x_dim, y_dim){
@@
 
-- Step Function
-  ![Sample](/cloud/project/image.jpg)
-
 - This is approached through an SIR model: Susceptible, Infected, Recovered. All change based on time as the function iterates through a set number of days. 
@@
 - Recovery and Incubation times ~ Gamma(alpha, beta), But in order to get whole number for days, we distribute them Possion(lambda)
+
+## What We are Trying to Simulate
+
+- Step Function
+  <!-- ![Sample](/cloud/project/image.jpg) -->
 
@@
 ```{r, echo=TRUE}
-get_bootstrap_cis <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, sample_size, ci_type='perc'){
-  #Create data frame to store samples
-  samps <- matrix(data=NA, nrow=sample_size, ncol=days + 1)
-  samps <- data.frame(samps)
-
-  #Create data frame to store confidence intervals
-  ci_df <- matrix(data=NA, nrow=days + 1, ncol=3)
-  ci_df <- data.frame(ci_df)
-
-  for(i in 1:sample_size){
-    samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist)
-  }
-
-  for(i in 1:ncol(samps)){
-    #Make sure column has more than one unique value
-    check <- (length(unique(samps[ ,i])) != 1)
-    if(check){
-    boot_obj <- boot(samps[ ,i], mean_func, 2000)
-    ci_obj <- boot.ci(boot_obj, conf = .95, type = ci_type)
-    ci_df[i, 1] <- ci_obj$percent[4]
-    ci_df[i, 2] <- ci_obj$t0
-    ci_df[i, 3] <- ci_obj$percent[5]
-    }else{ci_df[i, ] <- c(samps[1, i], samps[1, i], samps[1, i])}
-  }
-return(ci_df)
-}
-```
-
-## Boostrap plot of infected people
-
-\tiny
-```{r, echo = FALSE, output = TRUE}
-library(ggplot2)
-
-#Testing
-n=50
-y <- simulator(n,100,10,10,2,1)
-x <- 0:n
-
-#bootstrap
 mean_func <- function(daytuh, idx) {
@@
 }
+```
 
-plot_dat <- get_bootstrap_cis(days=50, num_subjects=100, x_dim=10, y_dim=10, I_0=2, inf_dist=1, sample_size=5)
+## Plot With Bootstrap 95% CI, 100 subjects
+
+\tiny
+```{r, echo = FALSE, output = TRUE}
+library(ggplot2)
+
+plot_dat <- get_bootstrap_cis(days=150, num_subjects=100, x_dim=20, y_dim=20, I_0=1, inf_dist=1, sample_size=20)
 
 ggplot() +
-  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
-  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
-  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red') +
+  geom_line(aes(x=1:151, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
+  geom_line(aes(x=1:151, y=plot_dat[ ,2])) +
+  geom_line(aes(x=1:151, y=plot_dat[ ,3]), linetype = 2, color = 'red') +
   xlab('Day') +
@@
 
-## Boostrap
+## Plot With Bootstrap 95% CI, 100 subjects
 
-```{r, echo = F}
-library(boot)
-starting_vals <- function(num_subjects, I_0, x_dim, y_dim){
+\tiny
+```{r}
+plot_dat2 <- get_bootstrap_cis(days=150, num_subjects=200, x_dim=20, y_dim=20, I_0=1, inf_dist=1, sample_size=20)
 
-  #Infect I_0 many starting subjects
-  subjects <- rep('S', num_subjects)
-  infect <- sample(x = 1:num_subjects, size=I_0, replace=FALSE)
-  subjects[infect] <- 'I'
-
-  #Storage for x, y starting positions for the subjects
-  start_x <- runif(n=num_subjects, min=0, max=x_dim)
-  start_y <- runif(n=num_subjects, min=0, max=y_dim)
-
-  inc_time <- rep(-1, num_subjects)
-  rec_days <- rep(-1, num_subjects)
-
-  #Put into a data frame
-  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects, rec_days, inc_time))
-  colnames(df)[1] <- 'x'
-  colnames(df)[2] <- 'y'
-  colnames(df)[3] <- 'subjects'
-  colnames(df)[4] <- 'incubation'
-  colnames(df)[5] <- 'recovery'
-
-  #Assign a recovery time to the infected subjects
-  df[df[,3] == 'I', 5] <- rpois(I_0, 14)
-
-  #Assign an incubation time to the infected subjects
-  df[df[,3] == 'I', 4] <- rpois(I_0, 5)
-
-  return(df)
-}
-
-#Random step length function
-get_step_length <- function(df, x_dim, y_dim){
-  step_lengths <- rnorm(n=nrow(df), mean=min(x_dim, y_dim)/4, sd=min(x_dim, y_dim)/12)
-  return(step_lengths)
-}
-
-#Random step direction function
-get_step_direction <- function(length_vec){
-  direction <- runif(n=length(length_vec), min=0, max=2*pi)
-}
-
-#Get delta_x, delta_y
-get_delts <- function(length_vec, direc_vec){
-  delta_x <- length_vec * cos(direc_vec)
-  delta_y <- length_vec * sin(direc_vec)
-  return(cbind(delta_x, delta_y))
-}
-
-#Function for getting updated coordinates
-update_coords <- function(og_df, delta_df){
-  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=5)
-  new_df <- data.frame(new_mx)
-  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
-  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
-  new_df[,3] <- og_df[,3]
-  new_df[,4] <- og_df[,4]
-  new_df[,5] <- og_df[,5]
-  colnames(new_df) <- c('x', 'y', 'subjects', 'incubation', 'recovery')
-  new_df
-}
-
-coord_checker <- function(og_df, new_df, x_dim, y_dim){
-  baddies <- NULL
-  for(i in 1:nrow(new_df)){
-    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'x']) < 0 | as.numeric(new_df[i, 'y']) > y_dim | as.numeric(new_df[i, 'y']) < 0){
-      baddies <- append(baddies, i)
-    }
-  }
-
-  if(is.null(baddies)){
-    return(new_df)
-  }else{
-  new_step <- get_step_length(new_df[i,], x_dim, y_dim)
-  new_direction <- get_step_direction(new_step)
-  new_change <- get_delts(new_step, new_direction)
-  new_df <- update_coords(og_df[baddies,], new_change)
-  full_df <- rbind(new_df, og_df[-baddies,])
-  return(coord_checker(og_df, full_df, x_dim, y_dim))
-  }
-}
-
-#Function for deciding if infections occurred
-infection_status <- function(state, mean_crit_dist){
-
-  current_infected <- state[state[,3]=='I' & state[,4] <= 0,]
-  current_suceptable <- state[state[,3]=='S',]
-  current_removed <- state[state[,3]=='R',]
-  current_non_contagious <- state[state[,3]=='I' & state[,4] > 0,]
-
-  #store new infection status
-  newly_infected <- NULL
-
-  #Check to see which susceptible subjects get infected
-  #For loop
-  if(nrow(current_suceptable) != 0 & nrow(current_infected) != 0){
-  for(i in 1:nrow(current_infected)){
-    for(j in 1:nrow(current_suceptable)){
-      x_i <- as.numeric(current_infected[i, 'x'])
-      y_i <- as.numeric(current_infected[i, 'y'])
-      x_s <- as.numeric(current_suceptable[j, 'x'])
-      y_s <- as.numeric(current_suceptable[j, 'y'])
-
-      crucial_distance <- rexp(1, 1/mean_crit_dist)
-
-      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
-      if(d <= crucial_distance){
-        newly_infected <- c(newly_infected, j)
-      }
-
-    }
-  }
-
-  current_suceptable[newly_infected, 3] <- 'I'
-  #Give incubation time
-  current_suceptable[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5)
-  #Give recovery time
-  current_suceptable[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)
-
-  new_state <- rbind(current_infected, current_suceptable, current_removed, current_non_contagious)
-  return(new_state)
-  }else{return(state)}
-}
-
-#simulation function
-simulator <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist){
-  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
-  end_day <- list()
-  num_cases <- rep(NA, days)
-  num_cases <- c(I_0, num_cases)
-  num_new_cases <- rep(NA, days)
-
-  for(i in 1:days){
-
-    if(i == 1){
-      step_size <- get_step_length(initial_data, x_dim, y_dim)
-      direction <- get_step_direction(step_size)
-      change <- get_delts(step_size, direction)
-
-      updated_positions <- update_coords(initial_data, change)
-      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
-      new_status <- infection_status(checked_positions, inf_dist)
-
-      #recovery time code
-      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
-      new_time <- as.numeric(not_recovered[, 5]) - 1
-      not_recovered[, 5] <- new_time
-      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
-      infected_0[, 3] <- rep('R', nrow(infected_0))
-      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
-      new_status = rbind(not_recovered, infected_0, not_infected)
-
-      #incubation time code
-      infected_people <- new_status[new_status[,3] == 'I',]
-      new_inc_time <- as.numeric(infected_people[,4]) - 1
-      infected_people[,4] <- new_inc_time
-      other_people <- new_status[new_status[,3] != 'I',]
-      new_status <- rbind(infected_people, other_people)
-
-      end_day[[i]] <- new_status
-
-      #Calculate number of new cases
-      num_cases[i+1] <- sum(new_status[,3]=='I')
-      num_new_cases[i] <- sum(new_status[,3]=='I') - I_0
-
-    }
-
-    else{
-      step_size <- get_step_length(initial_data, x_dim, y_dim)
-      direction <- get_step_direction(step_size)
-      change <- get_delts(step_size, direction)
-
-      updated_positions <- update_coords(end_day[[i-1]], change)
-      checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
-      new_status <- infection_status(checked_positions, inf_dist)
-
-      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
-      new_time <- as.numeric(not_recovered[, 5]) - 1
-      not_recovered[, 5] <- new_time
-      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
-      infected_0[, 3] <- rep('R', nrow(infected_0))
-      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
-      new_status = rbind(not_recovered, infected_0, not_infected)
-
-      #incubation time code
-      infected_people <- new_status[new_status[,3] == 'I',]
-      new_inc_time <- as.numeric(infected_people[,4]) - 1
-      infected_people[,4] <- new_inc_time
-      other_people <- new_status[new_status[,3] != 'I',]
-      new_status <- rbind(infected_people, other_people)
-
-      end_day[[i]] <- new_status
-
-      #Calculate number of new cases
-      num_cases[i+1] <- sum(new_status[,3]=='I')
-      num_new_cases[i] <- sum(new_status[,3]=='I') - num_cases[i-1]
-
-    }
-  }
-  return(num_cases)
-}
-
-#Testing
-df <- starting_vals(1000, 2, 1, 1)
-len <- get_step_length(df, 1, 1)
-dir <- get_step_direction(len)
-delts <- get_delts(len, dir)
-newdf <- update_coords(df, delts)
-coords <- coord_checker(df, newdf, 1, 1)
-new_status <- infection_status(coords, 8)
-
-set.seed(400)
-n=50
-y <- simulator(n,100,10,10,2,1)
-x <- 0:n
-
-#bootstrap
-mean_func <- function(daytuh, idx) {
-  mean(daytuh[idx])
-}
-
-get_bootstrap_cis <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, sample_size, ci_type='perc'){
-  #Create data frame to store samples
-  samps <- matrix(data=NA, nrow=sample_size, ncol=days + 1)
-  samps <- data.frame(samps)
-
-  #Create data frame to store confidence intervals
-  ci_df <- matrix(data=NA, nrow=days + 1, ncol=3)
-  ci_df <- data.frame(ci_df)
-
-  for(i in 1:sample_size){
-    samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist)
-  }
-
-  for(i in 1:ncol(samps)){
-    #Make sure column has more than one unique value
-    check <- (length(unique(samps[ ,i])) != 1)
-    if(check){
-    boot_obj <- boot(samps[ ,i], mean_func, 2000)
-    ci_obj <- boot.ci(boot_obj, conf = .95, type = ci_type)
-    ci_df[i, 1] <- ci_obj$percent[4]
-    ci_df[i, 2] <- ci_obj$t0
-    ci_df[i, 3] <- ci_obj$percent[5]
-    }else{ci_df[i, ] <- c(samps[1, i], samps[1, i], samps[1, i])}
-  }
-return(ci_df)
-}
-
-plot_dat <- get_bootstrap_cis(days=50, num_subjects=100, x_dim=10, y_dim=10, I_0=2, inf_dist=1, sample_size=5)
-
-daily_cases <- y
-boot.case <- boot(daily_cases, mean_func, 2000)
-
-plot(boot.case)
+ggplot() +
+  geom_line(aes(x=1:151, y=plot_dat2[ ,1]), linetype = 2, color = 'red') +
+  geom_line(aes(x=1:151, y=plot_dat2[ ,2])) +
+  geom_line(aes(x=1:151, y=plot_dat2[ ,3]), linetype = 2, color = 'red') +
+  xlab('Day') +
+  ylab('Number of Cases') +
+  ggtitle('Number of Covid-19 cases over time')
 
 ```
+
+## 'Flatten the Curve' - Pseudo Vaccination Effect
+
+\tiny
+```{r}
+ggplot() +
+  geom_line(aes(x=1:151, y=plot_dat[ ,2]), color='red') +
+  geom_line(aes(x=1:151, y=plot_dat2[ ,2]), color='blue') +
+  xlab('Day') +
+  ylab('Number of Cases') +
+  ggtitle('Number of Covid-19 cases over time')
+```
+
+## Pseudo Mask Effect
+
+\tiny
+```{r}
+plot_dat3 <- get_bootstrap_cis(days=150, num_subjects=100, x_dim=20, y_dim=20, I_0=1, inf_dist=0.5, sample_size=20)
+
+ggplot() +
+  geom_line(aes(x=1:151, y=plot_dat[ ,2]), color='red') +
+  geom_line(aes(x=1:151, y=plot_dat3[ ,2]), color='blue') +
+  xlab('Day') +
+  ylab('Number of Cases') +
+  ggtitle('Number of Covid-19 cases over time')
+```

### 2021-12-08 Stat 400 proj.Rmd
Avoiding an error
Added new graphs and cleaned up a bit

@@
 
-plot_dat <- get_bootstrap_cis(days=50, num_subjects=100, x_dim=10, y_dim=10, I_0=2, inf_dist=1, sample_size=5)
+plot_dat <- get_bootstrap_cis(days=50, num_subjects=3500, x_dim=100, y_dim=100, I_0=18, inf_dist=0.5, sample_size=20)
 
@@
 
-```
-
-```{r}
-#reported monte carlo summary data
-qd = c(0,25,50,75)
-pos = c(99.3,99.2,98.7,92.7)
-dncpv = c(69,53,46,33)
-dncpt = c(26,32,43,42)
-r0 = c(1.8,1.73,1.8,1.63)
-mcsum = cbind(qd,pos,dncpv,dncpt,r0)
-colnames(mcsum,c("Quarantine degree [%]",	"Percentage of size %",	"DNC peak value [cases]",	"DNC peaking time [days]",	"R0"))
-mcsum
 ```

### 2021-12-09 Stat 400 presentation.Rmd
Changed some titles
Set seed, and pdf

@@
 ```{r setup, include=FALSE}
+set.seed(400)
 knitr::opts_chunk$set(echo = FALSE)
@@
 - Step Function
-  <!-- ![Sample](/cloud/project/image.jpg) -->
+![Sample](/cloud/project/image.jpg)
 
@@
 
-## Plot With Bootstrap 95% CI, 100 subjects
+## Plot With Bootstrap 95% CI, 200 subjects
 
@@
 
-## 'Flatten the Curve' - Pseudo Vaccination Effect
+## Pseudo Vaccination Effect
 

### 2021-12-09 Stat 400 presentation.Rmd
typo's

@@
 
-- The goal of the study is to generate epidemiological based on natural mechanism of transmission of this disease assuming random interactions of a large-finite number of individuals in very short distance ranges.
+- The goal of the study is to generate epidemiological data based on the natural mechanism's of transmission of the virus assuming random interactions of a large-finite number of individuals in very short distance ranges.
 
@@
 
-- This is approached through an SIR model: Susceptible, Infected, Recovered. All change based on time as the function iterates through a set number of days. 
+- This is approached through an SIR model: Susceptible, Infected, Recovered. All change in the SIR model is based on time, as the function iterates through a set number of days. 
   - 0.5% of the initial subjects start out with the virus (infected)
-  - 99.5% subjects are susceptible
-  - 0% recovered
+  - 99.5% subjects are susceptible.
+  - 0% starting recovery.
 
-## Variables
+## Variables and Distributions
 
 - Factors to consider in the transmission of a virus. 
-  - What is the relationship and distribution between the infection probability and the physical distance
+  - What is the relationship and distribution between the infection probability and the physical distance?
   - High/low virus load, varying physical distances, ineffective vs effective mask wearing. 
@@
 - Based on real epidemiological data analysis, these encompassing factors will be distributed Exponential(rate = lambda)
-- Recovery and Incubation times ~ Gamma(alpha, beta), But in order to get whole number for days, we distribute them Possion(lambda)
+- Recovery and Incubation times ~ Gamma(alpha, beta), But in order to get whole number for our outputted days, we chose to distribute them Possion(lambda)
 

### 2021-12-12 Paper.Rmd
Started the motivation

---
title: "Paper"
author: "Nathan Hemenway"
date: "12/12/2021"
output: pdf_document
---

Motivation
The motivation behind our Monte Carlo Covid-19 simulator is to be able to better understand the spread of Covid-19. Through Monte Carlo simulation, we can observe what affect variables such as starting infected population, total population, physical space, infection distance, as well as incubation and recovery times have on the long term spread of the disease. These variables can be easily adjusted in our code to give different scenarios. The way we measure the effect changes in the aforementioned variables is by looking at the difference between the daily number of cases. This can be well visualized in a plot giving number of infected people per day. At the beginning of the Covid-19 pandemic, there were public health measures put into place that aimed at 'flattening' the curve of daily cases of Covid-19. We are interested in seeing what effect different policies and population characteristics have on the plot of daily Covid-19 infections. If we can understand what affect different input variables have on the outcome of the pandemic, we can possibly make better policy decisions regarding Covid-19.

### 2021-12-13 Paper.Rmd
motivation

@@
 
-Motivation
+Background:
+The paper "Novel approach for Monte Carlo simulation of the new COVID-19 spread dynamics aim's to investigate the transmission and incubation random processes of COVID-19.
+The goal of the study is to generate epidemiological data based on the natural mechanism's of transmission of the virus assuming random interactions of a large-finite number of individuals in very short distance ranges.
+A few important assumptions that were made were in how the transmission of the virus occurs when the physical distance between individuals decreases to where the probability of transmission converges to one, asymptotically.
+Their model defined the steps of movement in a defined space as a randomly assigned process.
+They approached this through the SIR model; A model defining Susceptible, Infected, Recovered individuals.
+All change in the SIR model is based on time, as the function iterates through a set number of days.
+They started with a 0.5% infection rate and simulation daily infection counts over a range of time.
+In order to capture many factors in the transmission including the relationship between infection probability between physical distance, effective and ineffective mask wearing, and environmental conditions they distributed these factors Exponential(rate = lambda).
+Initial recovery and incubation times were distributed Gamma(alpha,beta).
+
+Motivation:
 The motivation behind our Monte Carlo Covid-19 simulator is to be able to better understand the spread of Covid-19.
@@
 If we can understand what affect different input variables have on the outcome of the pandemic, we can possibly make better policy decisions regarding Covid-19.
+
+Methodology:
+
+Results:

### 2021-12-13 Stat 400 proj.Rmd
Vaccine Status

@@
 #create starting positions and state function
-starting_vals <- function(num_subjects, I_0, x_dim, y_dim){
+starting_vals <- function(num_subjects, I_0, x_dim, y_dim, prop_vac){
 
@@
   subjects[infect] <- 'I'
+
+  #Determining if a person is vaccinated
+  vac_ppl <- sample(x = 1:num_subjects, size = round(prop_vac * num_subjects), replace = F)
+  vac_vec <- rep(F , num_subjects)
+  vac_vec[vac_ppl] <- T
 
@@
   #Put into a data frame
-  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects, rec_days, inc_time))
+  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects, rec_days, inc_time, vac_vec))
   colnames(df)[1] <- 'x'
@@
   colnames(df)[5] <- 'recovery'
+  colnames(df)[6] <- 'vaccine'
 
@@
   new_df[,5] <- og_df[,5]
-  colnames(new_df) <- c('x', 'y', 'subjects', 'incubation', 'recovery')
+  new_df[,6] <- og_df[,6]
+  colnames(new_df) <- c('x', 'y', 'subjects', 'incubation', 'recovery', 'vaccine')
   new_df
@@
       crucial_distance <- rexp(1, 1/mean_crit_dist)
+      vaccine_status <- current_suceptable[j, 'vaccine']
+      if(vaccine_status == T) {
+        vac_eff <- as.logical(rbinom(1,1,.8))
+      }
+      else {
+        vac_eff <- F
+      }
 
       d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
-      if(d <= crucial_distance){
+      if(d <= crucial_distance & vac_eff == F){
         newly_infected <- c(newly_infected, j)
@@
 #simulation function
-simulator <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist){
-  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
+simulator <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, prop_vac){
+  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0, prop_vac = prop_vac)
   end_day <- list()
@@
 #Testing
-df <- starting_vals(1000, 2, 1, 1)
+df <- starting_vals(1000, 2, 1, 1, .8)
 len <- get_step_length(df, 1, 1)
@@
 n=50
-y <- simulator(n,100,10,10,2,1)
+y <- simulator(n,100,10,10,2,1,.95)
 x <- 0:n
 
-ggplot() +
+plot <- ggplot() +
   geom_line(aes(x=x, y=y)) +

### 2021-12-13 Stat 400 proj.Rmd
Added prop_vac to bootstrap and removed some random extra lines

@@
       d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
-      if(d <= crucial_distance & vac_eff == F){
+      if(d <= crucial_distance & (vac_eff == F)){
         newly_infected <- c(newly_infected, j)
       }
-
     }
@@
 n=50
-y <- simulator(n,100,10,10,2,1,.95)
-x <- 0:n
+y <- simulator(100, 1000, 1, 1, 5, 0.005, 0)
+x <- 0:100
 
-plot <- ggplot() +
+ggplot() +
   geom_line(aes(x=x, y=y)) +
@@
 
-get_bootstrap_cis <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, sample_size, ci_type='perc'){
+get_bootstrap_cis <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, sample_size, ci_type='perc', prop_vac = 0){
   #Create data frame to store samples
@@
   for(i in 1:sample_size){
-    samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist)
+    samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist, prop_vac)
   }
@@
 
-plot_dat <- get_bootstrap_cis(days=50, num_subjects=3500, x_dim=100, y_dim=100, I_0=18, inf_dist=0.5, sample_size=20)
+plot_dat <- get_bootstrap_cis(days=50, num_subjects=100, x_dim=1, y_dim=1, I_0=5, inf_dist=0.5, sample_size=20, prop_vac = 0.8)
 
@@
   geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red')
-
-daily_cases <- y
-boot.case <- boot(daily_cases, mean_func, 2000)
-
-plot(boot.case)
-
-boot.ci(boot.case, conf = .95, type = c("perc", "basic", "norm", "bca"))
 

### 2021-12-13 Paper.Rmd
Added code needed to create plots. Started methodology and small town plots.

@@
 ---
+
+```{r, include=FALSE}
+library(tidyverse)
+library(ggplot2)
+library(boot)
+#create starting positions and state function
+starting_vals <- function(num_subjects, I_0, x_dim, y_dim, prop_vac){
+
+  #Infect I_0 many starting subjects
+  subjects <- rep('S', num_subjects)
+  infect <- sample(x = 1:num_subjects, size=I_0, replace=FALSE)
+  subjects[infect] <- 'I'
+
+  #Determining if a person is vaccinated
+  vac_ppl <- sample(x = 1:num_subjects, size = round(prop_vac * num_subjects), replace = F)
+  vac_vec <- rep(F , num_subjects)
+  vac_vec[vac_ppl] <- T
+
+  #Storage for x, y starting positions for the subjects
+  start_x <- runif(n=num_subjects, min=0, max=x_dim)
+  start_y <- runif(n=num_subjects, min=0, max=y_dim)
+
+  inc_time <- rep(-1, num_subjects)
+  rec_days <- rep(-1, num_subjects)
+
+  #Put into a data frame
+  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects, rec_days, inc_time, vac_vec))
+  colnames(df)[1] <- 'x'
+  colnames(df)[2] <- 'y'
+  colnames(df)[3] <- 'subjects'
+  colnames(df)[4] <- 'incubation'
+  colnames(df)[5] <- 'recovery'
+  colnames(df)[6] <- 'vaccine'
+
+  #Assign a recovery time to the infected subjects
+  df[df[,3] == 'I', 5] <- rpois(I_0, 14)
+
+  #Assign an incubation time to the infected subjects
+  df[df[,3] == 'I', 4] <- rpois(I_0, 5)
+
+  return(df)
+}
+
+#Random step length function
+get_step_length <- function(df, x_dim, y_dim){
+  step_lengths <- rnorm(n=nrow(df), mean=min(x_dim, y_dim)/4, sd=min(x_dim, y_dim)/12)
+  return(step_lengths)
+}
+
+#Random step direction function
+get_step_direction <- function(length_vec){
+  direction <- runif(n=length(length_vec), min=0, max=2*pi)
+}
+
+#Get delta_x, delta_y
+get_delts <- function(length_vec, direc_vec){
+  delta_x <- length_vec * cos(direc_vec)
+  delta_y <- length_vec * sin(direc_vec)
+  return(cbind(delta_x, delta_y))
+}
+
+#Function for getting updated coordinates
+update_coords <- function(og_df, delta_df){
+  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=5)
+  new_df <- data.frame(new_mx)
+  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
+  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
+  new_df[,3] <- og_df[,3]
+  new_df[,4] <- og_df[,4]
+  new_df[,5] <- og_df[,5]
+  new_df[,6] <- og_df[,6]
+  colnames(new_df) <- c('x', 'y', 'subjects', 'incubation', 'recovery', 'vaccine')
+  new_df
+}
+
+coord_checker <- function(og_df, new_df, x_dim, y_dim){
+  baddies <- NULL
+  for(i in 1:nrow(new_df)){
+    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'x']) < 0 | as.numeric(new_df[i, 'y']) > y_dim | as.numeric(new_df[i, 'y']) < 0){
+      baddies <- append(baddies, i)
+    }
+  }
+
+  if(is.null(baddies)){
+    return(new_df)
+  }else{
+  new_step <- get_step_length(new_df[i,], x_dim, y_dim)
+  new_direction <- get_step_direction(new_step)
+  new_change <- get_delts(new_step, new_direction)
+  new_df <- update_coords(og_df[baddies,], new_change)
+  full_df <- rbind(new_df, og_df[-baddies,])
+  return(coord_checker(og_df, full_df, x_dim, y_dim))
+  }
+}
+
+#Function for deciding if infections occurred
+infection_status <- function(state, mean_crit_dist){
+
+  current_infected <- state[state[,3]=='I' & state[,4] <= 0,]
+  current_suceptable <- state[state[,3]=='S',]
+  current_removed <- state[state[,3]=='R',]
+  current_non_contagious <- state[state[,3]=='I' & state[,4] > 0,]
+
+  #store new infection status
+  newly_infected <- NULL
+
+  #Check to see which susceptible subjects get infected
+  #For loop
+  if(nrow(current_suceptable) != 0 & nrow(current_infected) != 0){
+  for(i in 1:nrow(current_infected)){
+    for(j in 1:nrow(current_suceptable)){
+      x_i <- as.numeric(current_infected[i, 'x'])
+      y_i <- as.numeric(current_infected[i, 'y'])
+      x_s <- as.numeric(current_suceptable[j, 'x'])
+      y_s <- as.numeric(current_suceptable[j, 'y'])
+
+      crucial_distance <- rexp(1, 1/mean_crit_dist)
+      vaccine_status <- current_suceptable[j, 'vaccine']
+      if(vaccine_status == T) {
+        vac_eff <- as.logical(rbinom(1,1,.8))
+      }
+      else {
+        vac_eff <- F
+      }
+
+      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
+      if(d <= crucial_distance & (vac_eff == F)){
+        newly_infected <- c(newly_infected, j)
+      }
+    }
+  }
+
+  current_suceptable[newly_infected, 3] <- 'I'
+  #Give incubation time
+  current_suceptable[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5)
+  #Give recovery time
+  current_suceptable[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)
+
+  new_state <- rbind(current_infected, current_suceptable, current_removed, current_non_contagious)
+  return(new_state)
+  }else{return(state)}
+}
+
+#simulation function
+simulator <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, prop_vac){
+  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0, prop_vac = prop_vac)
+  end_day <- list()
+  num_cases <- rep(NA, days)
+  num_cases <- c(I_0, num_cases)
+  num_new_cases <- rep(NA, days)
+
+  for(i in 1:days){
+
+    if(i == 1){
+      step_size <- get_step_length(initial_data, x_dim, y_dim)
+      direction <- get_step_direction(step_size)
+      change <- get_delts(step_size, direction)
+
+      updated_positions <- update_coords(initial_data, change)
+      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
+      new_status <- infection_status(checked_positions, inf_dist)
+
+      #recovery time code
+      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
+      new_time <- as.numeric(not_recovered[, 5]) - 1
+      not_recovered[, 5] <- new_time
+      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
+      infected_0[, 3] <- rep('R', nrow(infected_0))
+      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
+      new_status = rbind(not_recovered, infected_0, not_infected)
+
+      #incubation time code
+      infected_people <- new_status[new_status[,3] == 'I',]
+      new_inc_time <- as.numeric(infected_people[,4]) - 1
+      infected_people[,4] <- new_inc_time
+      other_people <- new_status[new_status[,3] != 'I',]
+      new_status <- rbind(infected_people, other_people)
+
+      end_day[[i]] <- new_status
+
+      #Calculate number of new cases
+      num_cases[i+1] <- sum(new_status[,3]=='I')
+      num_new_cases[i] <- sum(new_status[,3]=='I') - I_0
+
+    }
+
+    else{
+      step_size <- get_step_length(initial_data, x_dim, y_dim)
+      direction <- get_step_direction(step_size)
+      change <- get_delts(step_size, direction)
+
+      updated_positions <- update_coords(end_day[[i-1]], change)
+      checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
+      new_status <- infection_status(checked_positions, inf_dist)
+
+      not_recovered <- new_status[as.numeric(new_status[, 5]) > 0, ]
+      new_time <- as.numeric(not_recovered[, 5]) - 1
+      not_recovered[, 5] <- new_time
+      infected_0 <- new_status[as.numeric(new_status[, 5]) == 0, ]
+      infected_0[, 3] <- rep('R', nrow(infected_0))
+      not_infected = new_status[as.numeric(new_status[, 5]) < 0, ]
+      new_status = rbind(not_recovered, infected_0, not_infected)
+
+      #incubation time code
+      infected_people <- new_status[new_status[,3] == 'I',]
+      new_inc_time <- as.numeric(infected_people[,4]) - 1
+      infected_people[,4] <- new_inc_time
+      other_people <- new_status[new_status[,3] != 'I',]
+      new_status <- rbind(infected_people, other_people)
+
+      end_day[[i]] <- new_status
+
+      #Calculate number of new cases
+      num_cases[i+1] <- sum(new_status[,3]=='I')
+      num_new_cases[i] <- sum(new_status[,3]=='I') - num_cases[i-1]
+
+    }
+  }
+  return(num_cases)
+}
+
+#Testing
+df <- starting_vals(1000, 2, 1, 1, .8)
+len <- get_step_length(df, 1, 1)
+dir <- get_step_direction(len)
+delts <- get_delts(len, dir)
+newdf <- update_coords(df, delts)
+coords <- coord_checker(df, newdf, 1, 1)
+coords
+new_status <- infection_status(coords, 8)
+new_status
+
+set.seed(400)
+n=50
+y <- simulator(100, 1000, 1, 1, 5, 0.005, 0)
+x <- 0:100
+
+ggplot() +
+  geom_line(aes(x=x, y=y)) +
+  xlab('Day') +
+  ylab('Number of Cases') +
+  ggtitle('Number of Covid-19 cases over time')
+
+#bootstrap
+mean_func <- function(daytuh, idx) {
+  mean(daytuh[idx])
+}
+
+get_bootstrap_cis <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, sample_size, ci_type='perc', prop_vac = 0){
+  #Create data frame to store samples
+  samps <- matrix(data=NA, nrow=sample_size, ncol=days + 1)
+  samps <- data.frame(samps)
+
+  #Create data frame to store confidence intervals
+  ci_df <- matrix(data=NA, nrow=days + 1, ncol=3)
+  ci_df <- data.frame(ci_df)
+
+  for(i in 1:sample_size){
+    samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist, prop_vac)
+  }
+
+  for(i in 1:ncol(samps)){
+    #Make sure column has more than one unique value
+    check <- (length(unique(samps[ ,i])) != 1)
+    if(check){
+    boot_obj <- boot(samps[ ,i], mean_func, 2000)
+    ci_obj <- boot.ci(boot_obj, conf = .95, type = ci_type)
+    ci_df[i, 1] <- ci_obj$percent[4]
+    ci_df[i, 2] <- ci_obj$t0
+    ci_df[i, 3] <- ci_obj$percent[5]
+    }else{ci_df[i, ] <- c(samps[1, i], samps[1, i], samps[1, i])}
+  }
+return(ci_df)
+}
+
+plot_dat <- get_bootstrap_cis(days=50, num_subjects=100, x_dim=1, y_dim=1, I_0=5, inf_dist=0.5, sample_size=20, prop_vac = 0.8)
+
+ggplot() +
+  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
+  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
+  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red')
+
+```
 
@@
 Methodology:
+To start, we created functions that generate a random step length.
+This was done by using a normal distribution with a mean and standard deviation of the minimum of the dimensions divided by four and twelve respectively.
+Once we have a step length we generate a step direction from a uniform(0, 2$\pi$) distribution.
+This is the direction angle in radians.
+From these two pieces of information, we can then update the coordinate values in the update_coords function.
 
 Results:
+Going to look at 1x1 with 1000 people: represents small town population density with 0.5% intial infected. Will look at distances between 0.001 (6 ft) to 0.01 (60 ft?) and see what differences exist.
+```{r, cache=TRUE}
+plot_dat <- get_bootstrap_cis(days=150, num_subjects=1000, x_dim=1, y_dim=1, I_0=5, inf_dist=0.01, sample_size=20, prop_vac = 0.8)
+
+ggplot() +
+  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
+  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
+  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red')
+
+```

### 2021-12-14 Paper.Rmd
Worked on methodology

@@
 
-#Testing
-df <- starting_vals(1000, 2, 1, 1, .8)
-len <- get_step_length(df, 1, 1)
-dir <- get_step_direction(len)
-delts <- get_delts(len, dir)
-newdf <- update_coords(df, delts)
-coords <- coord_checker(df, newdf, 1, 1)
-coords
-new_status <- infection_status(coords, 8)
-new_status
-
-set.seed(400)
-n=50
-y <- simulator(100, 1000, 1, 1, 5, 0.005, 0)
-x <- 0:100
-
-ggplot() +
-  geom_line(aes(x=x, y=y)) +
-  xlab('Day') +
-  ylab('Number of Cases') +
-  ggtitle('Number of Covid-19 cases over time')
-
 #bootstrap
@@
 
-plot_dat <- get_bootstrap_cis(days=50, num_subjects=100, x_dim=1, y_dim=1, I_0=5, inf_dist=0.5, sample_size=20, prop_vac = 0.8)
-
-ggplot() +
-  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
-  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
-  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red')
-
 ```
@@
 To start, we created functions that generate a random step length.
-This was done by using a normal distribution with a mean and standard deviation of the minimum of the dimensions divided by four and twelve respectively.
-Once we have a step length we generate a step direction from a uniform(0, 2$\pi$) distribution.
-This is the direction angle in radians.
-From these two pieces of information, we can then update the coordinate values in the update_coords function.
+This was done using the rnorm() function for the normal distribution with a mean and standard deviation of the minimum of the dimensions divided by four and twelve respectively.
+Once we have a step length we generate a step direction from a uniform(0, 2$\pi$) distribution using runif().
+This gives the direction angle in radians.
+From these two pieces of information, we can then update the coordinate values in the update_coords function by adding the change to the original x and y values.
+This is done using trigonometry equations for the legs of a triangle given the hypotenuse and angle.
+
+The obvious problem that arises when using this approach is that subjects will inevitably leave the specified space they are supposed to remain in.
+For example, if we want the subjects to stay in a [0, 1] x [0, 1] square, and we let them move in any direction, the mean step distance will be 0.25, so it would only take a centered subject a couple moves in the same direction before they leave the space.
+The solution we employed was to check and see whether a certain move would put a subject out of bounds, and if so re-sample a different move, then repeat for all subjects until they are all within bounds.
+This is what the coord_checker() function does.
+
+After moving the subjects randomly in the given space, the next step in the simulation is to check if any infected subjects have infected others.
+This is done via the infection_status() function.
+The first thing we did was subset the subjects into different data frames by infection status.
+Then we can check how far the susceptible subjects are from the infected subjects.
+If they come within a crucial distance generated using an exponential distribution, we infect the susceptible subject.
 

### 2021-12-14 Paper.Rmd
Tried running bootstrap

@@
 ```{r, cache=TRUE}
-plot_dat <- get_bootstrap_cis(days=150, num_subjects=1000, x_dim=1, y_dim=1, I_0=5, inf_dist=0.01, sample_size=20, prop_vac = 0.8)
+plot_dat <- get_bootstrap_cis(days=100, num_subjects=100, x_dim=1, y_dim=1, I_0=5, inf_dist=0.1, sample_size=20, prop_vac = 0.8)
 
 ggplot() +
-  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
-  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
-  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red')
+  geom_line(aes(x=1:101, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
+  geom_line(aes(x=1:101, y=plot_dat[ ,2])) +
+  geom_line(aes(x=1:101, y=plot_dat[ ,3]), linetype = 2, color = 'red')
 

### 2021-12-14 Paper.Rmd
Added some plots and more to methodology

--- 2021-12-14 Paper.Rmd
@@
 Then we can check how far the susceptible subjects are from the infected subjects.
-If they come within a crucial distance generated using an exponential distribution, we infect the susceptible subject.
+If they come within a crucial distance generated using an exponential distribution, then they are vulnerable to infection.
+Then if the susceptible person is vaccinated, we generate a binomial(1, 0.8) random variable to determine if the vaccine was effective in preventing infection.
+The third condition necessary for infection to occur is that the incubation period of the virus has passed for the infected person.
+The incubation length is assigned upon infection using rpois(1, 5), and decreases by one each day until it reaches zero.
+If binomial vaccine effect returns false, and the susceptible person is within the generated crucial distance of the infected person, and the infected person is past the incubation period, then the suceptible person becomes infected.
+Once infected, a subject is assigned a recovery time using rpois(1, 14).
+For each iteration in the simulator, one is subtracted from the recovery time.
+Once recovery time reaches zero, the infection status of the subject is changed from infected to recovered.
 
 Results:
-Going to look at 1x1 with 1000 people: represents small town population density with 0.5% intial infected. Will look at distances between 0.001 (6 ft) to 0.01 (60 ft?) and see what differences exist.
+Going to look at 1x1 with 1000 people: represents small town population density with 0.5% intial infected.
+Will look at distances between 0.001 (6 ft) to 0.01 (60 ft?) and see what differences exist.
+Assuming no vaccinations.
 ```{r, cache=TRUE}
-plot_dat <- get_bootstrap_cis(days=150, num_subjects=1000, x_dim=1, y_dim=1, I_0=5, inf_dist=0.01, sample_size=20, prop_vac = 0.8)
+set.seed(400)
+#~6ft apart
+y <- simulator(150, 1000, 1, 1, 5, 0.001, 0)
+x <- 0:150
 
 ggplot() +
-  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
-  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
-  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red')
+  geom_line(aes(x=x, y=y)) +
+  xlab('Day') +
+  ylab('Number of Cases') +
+  ggtitle('Number of Covid-19 cases over time')
+
+#~26 ft apart
+y <- simulator(150, 1000, 1, 1, 5, 0.005, 0)
+x <- 0:150
+
+ggplot() +
+  geom_line(aes(x=x, y=y)) +
+  xlab('Day') +
+  ylab('Number of Cases') +
+  ggtitle('Number of Covid-19 cases over time')
+
+#~ 53ft apart
+y <- simulator(150, 1000, 1, 1, 5, 0.01, 0)
+x <- 0:150
+
+ggplot() +
+  geom_line(aes(x=x, y=y)) +
+  xlab('Day') +
+  ylab('Number of Cases') +
+  ggtitle('Number of Covid-19 cases over time')
 
 ```
+Write about difference between different crucial distances here.
+
+```{r}
+set.seed(400)
+plot_dat1 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=20, prop_vac = 0)
+
+ggplot() +
+  geom_line(aes(x=1:51, y=plot_dat1[ ,1]), linetype = 2, color = 'red') +
+  geom_line(aes(x=1:51, y=plot_dat1[ ,2])) +
+  geom_line(aes(x=1:51, y=plot_dat1[ ,3]), linetype = 2, color = 'red')
+
+plot_dat2 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=20, prop_vac = 0.5)
+
+ggplot() +
+  geom_line(aes(x=1:51, y=plot_dat2[ ,1]), linetype = 2, color = 'red') +
+  geom_line(aes(x=1:51, y=plot_dat2[ ,2])) +
+  geom_line(aes(x=1:51, y=plot_dat2[ ,3]), linetype = 2, color = 'red')
+
+plot_dat3 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=20, prop_vac = 0.8)
+
+ggplot() +
+  geom_line(aes(x=1:51, y=plot_dat3[ ,1]), linetype = 2, color = 'red') +
+  geom_line(aes(x=1:51, y=plot_dat3[ ,2])) +
+  geom_line(aes(x=1:51, y=plot_dat3[ ,3]), linetype = 2, color = 'red')
+
+plot_dat4 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=20, prop_vac = 0.95)
+
+ggplot() +
+  geom_line(aes(x=1:51, y=plot_dat4[ ,1]), linetype = 2, color = 'red') +
+  geom_line(aes(x=1:51, y=plot_dat4[ ,2])) +
+  geom_line(aes(x=1:51, y=plot_dat4[ ,3]), linetype = 2, color = 'red')
+
+#plot all vaccine curves
+ggplot() +
+  geom_line(aes(x=1:51, y=plot_dat1[ ,2])) +
+  geom_line(aes(x=1:51, y=plot_dat2[ ,2]), color='red') +
+  geom_line(aes(x=1:51, y=plot_dat3[ ,2]), color='blue') +
+  geom_line(aes(x=1:51, y=plot_dat4[ ,2]), color='green')
+
+```

### 2021-12-14 Paper.Rmd
Minor edit

@@
 
+Compare different vaccination rates
 ```{r}

### 2021-12-15 Paper.Rmd
Wrote about the simulator function

@@
 
+All the above culminates in the simulator function.
+This function takes in the given area, number of subjects, number of starting infected subjects, mean infection distance, number of days for the simulation, and proportion of subjects that are vaccinated.
+Using a for loop for each day, the function generates new positions for the subjects, and returns how many people have been infected per day.
+This can be used to generate a plot for the number of daily cases by plotting day on the x axis and number of cases on the y axis.
+If you run the simulation repeatedly, you can create a bootstrap confidence interval for the mean number of cases each day.
+This is done in the get_bootstrap_cis function.
+The function then returns the bootstrap confidence intervals as well as the mean for each day for a given sample size.
+For our purposes we used a sample size of 20 due to the computational burden of repeatedly running simulations.
+This data can be used to create a plot of the mean number of cases per day as well as 95% bootstrap confidence intervals for each day.
+
 Results:

### 2021-12-15 Paper.Rmd
Changed recovery times to gamma

@@
   #Assign a recovery time to the infected subjects
-  df[df[,3] == 'I', 5] <- rpois(I_0, 14)
+  df[df[,3] == 'I', 5] <- round(rgamma(n=I_0, 6, 2/3))
 
@@
   #Give recovery time
-  current_suceptable[newly_infected, 5] <- rpois(n=length(newly_infected), lambda = 14)
+  current_suceptable[newly_infected, 5] <- round(rgamma(n=length(newly_infected), 6, 2/3))
 
@@
     samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist, prop_vac)
+    print(i)
   }
@@
 This data can be used to create a plot of the mean number of cases per day as well as 95% bootstrap confidence intervals for each day.
+We decided to use percentile bootstrap confidence intervals since they are the most interpretable.
 
@@
 #~ 53ft apart
-y <- simulator(150, 1000, 1, 1, 5, 0.01, 0)
-x <- 0:150
+plot_dat <- get_bootstrap_cis(days=150, num_subjects=1000, x_dim=1, y_dim=1, I_0=5, inf_dist=0.01, sample_size=20, prop_vac = 0)
 
 ggplot() +
-  geom_line(aes(x=x, y=y)) +
-  xlab('Day') +
-  ylab('Number of Cases') +
-  ggtitle('Number of Covid-19 cases over time')
+  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
+  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
+  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red')
 

### 2021-12-15 Paper.Rmd
Wrote some paragraphs in the results section. I also added labels to the graphs that didn't have them. Let me know if you need me to write any more or change what I have.

@@
 title: "Paper"
-author: "Nathan Hemenway"
+author: "Nathan Hemenway, Mark Hinds, Ian Hall"
 date: "12/12/2021"
@@
   geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
-  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red')
+  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red') + 
+  labs(x="Day", y="People infected")
 
 ```
-Write about difference between different crucial distances here.
+We started with 5 infected people in each simulation.
+In our first two simulations we were attempting to simulate a 6 and 26 foot infection distance.
+As you can see from the first two plots above, no one was infected from the 5 initial people who were infected.
+This is because in these examples we were trying to simulate a small town with a low population density.
+This is supposed to represent 1000 people in a town that is 36 million square feet or about 1.3 square miles.
+Since the population density is so low, it is extremely unlikely for two people to come in close enough contact to contract Covid-19 in our simulation.
+Our simulation does have its limitations and this may not be realistic.
+Our simulator is assuming every person is independent and randomly moves around from day to day.
+This doesn't account for hanging out with friends or going home to your family which are common situations where contracting Covid-19 is much more likely.
+Accounting for these factors might be possible, but its beyond the scope of this project.
+In our third simulation, we used a bootstrap confidence interval for an infection distance of about 60 feet.
+This distance was finally large enough that people still got infected despite the low population density.
+Based on the plot, the number of infected people will peak around 50 days and then slowly decrease as the majority of people start to recover and gain immunity.
+This simulation looks more realistic and follows the infection trend that viruses generally have.
 
@@
   geom_line(aes(x=1:51, y=plot_dat1[ ,2])) +
-  geom_line(aes(x=1:51, y=plot_dat1[ ,3]), linetype = 2, color = 'red')
+  geom_line(aes(x=1:51, y=plot_dat1[ ,3]), linetype = 2, color = 'red') + 
+  labs(x="Day", y="People infected")
 
@@
   geom_line(aes(x=1:51, y=plot_dat2[ ,2])) +
-  geom_line(aes(x=1:51, y=plot_dat2[ ,3]), linetype = 2, color = 'red')
+  geom_line(aes(x=1:51, y=plot_dat2[ ,3]), linetype = 2, color = 'red') + 
+  labs(x="Day", y="People infected")
 
@@
   geom_line(aes(x=1:51, y=plot_dat3[ ,2])) +
-  geom_line(aes(x=1:51, y=plot_dat3[ ,3]), linetype = 2, color = 'red')
+  geom_line(aes(x=1:51, y=plot_dat3[ ,3]), linetype = 2, color = 'red') + 
+  labs(x="Day", y="People infected")
 
@@
   geom_line(aes(x=1:51, y=plot_dat4[ ,2])) +
-  geom_line(aes(x=1:51, y=plot_dat4[ ,3]), linetype = 2, color = 'red')
+  geom_line(aes(x=1:51, y=plot_dat4[ ,3]), linetype = 2, color = 'red') + 
+  labs(x="Day", y="People infected")
 
@@
   geom_line(aes(x=1:51, y=plot_dat3[ ,2]), color='blue') +
-  geom_line(aes(x=1:51, y=plot_dat4[ ,2]), color='green')
+  geom_line(aes(x=1:51, y=plot_dat4[ ,2]), color='green') + 
+  labs(x="Day", y="People infected")
 
 ```
+In the previous three simulations we assumed that no one was vaccinated, but we also wanted to look at how a vaccine would effect the spread of Covid-19.
+In these simulations we looked at 200 people with the same dimension parameters as before, but with only one person initially infected.
+We increased the infection distance since 200 people in a 1.3 square mile area is an even lower population density than before.
+All the parameters were held the same other than the vaccination rate for these simulations.
+The vaccine rates of the four examples were: 0, .5, .8, and .95.
+In the plot that shows the number of infected for each vaccination rate, black is 0 vaccinated, red is .5, blue is .8, and green is .95.
+As we would expect, when no one is vaccinated, the number of infected people peaks and falls much faster than when some people are vaccinated.
+It only took around 15 days to peak and nearly everyone was recovered by day 30.
+When no one was vaccinated it took much less time to get sick, but people also were recovered faster because everyone already had the virus.
+This is the idea of herd immunity that is often talked about, but it poses a massive problem with the hospitals.
+If everyone gets sick in a short period of time, hospitals can get overwhelmed and the death tolls can skyrocket due to lack of equipment and staff.
+Vaccinations aren't perfect, but they can help flatten the curve so the infection numbers don't peak as fast and also reduce the severity of the symptoms so less people need to be hospitalized.
+It is still possible to contract Covid-19 while vaccinated, but it is much less likely.
+As you can see in the last plot, as the vaccination rate increased, the longer it took for the cases to peak.
+The peak was also much lower than when no one was vaccinated and it took longer for the cases to completely disappear since people were being infected slower.
+This shows that a higher vaccination rate helps slow down the spread of Covid-19 even if it can't completely prevent it.

### 2021-12-16 Paper.Rmd
sources

--- 2021-12-15 Paper.Rmd
@@
 
-  #Assign an incubation time to the infected subjects
-  df[df[,3] == 'I', 4] <- rpois(I_0, 5)
+  #Assign an incubation time to the infected subjects (Source)
+  df[df[,3] == 'I', 4] <- rpois(I_0, 5.15)
 
@@
 ```
+
+Bibliography:
+
+[1] S.
+Maltezos and A.
+Georgakopoulou, “Novel approach for Monte Carlo simulation of the new COVID-19 spread dynamics,” Infection, Genetics and Evolution, vol.
+92, p.
+104896, 2021, doi: https://doi.org/10.1016/j.meegid.2021.104896.
+
+[2] Lauer SA, Grantz KH, Bi Q, Jones FK, Zheng Q, Meredith HR, Azman AS, Reich NG, Lessler J.
+"The Incubation Period of Coronavirus Disease 2019 (COVID-19) From Publicly Reported Confirmed Cases: Estimation and Application." Ann Intern Med.
+2020 May 5;172(9):577-582.
+doi: 10.7326/M20-0504.
+Epub 2020 Mar 10.
+PMID: 32150748; PMCID: PMC7081172.

### 2021-12-16 Paper.Rmd

--- 2021-12-15 Paper.Rmd
@@
 Initial recovery and incubation times were distributed Gamma(alpha,beta).
+(Source 1)
 
@@
 ```
+
 In the previous three simulations we assumed that no one was vaccinated, but we also wanted to look at how a vaccine would effect the spread of Covid-19.
@@
 This shows that a higher vaccination rate helps slow down the spread of Covid-19 even if it can't completely prevent it.
+
+Bibliography:
+
+[1] Maltezos, S., & Georgakopoulou, A.
+(2021).
+Novel approach for Monte Carlo simulation of the new COVID-19 spread dynamics.
+Infection, Genetics and Evolution, 92, 104896.
+https://doi.org/10.1016/j.meegid.2021.104896
+
+[2] Lauer, S.
+A., Grantz, K.
+H., Bi, Q., Jones, F.
+K., Zheng, Q., Meredith, H.
+R., Azman, A.
+S., Reich, N.
+G., & Lessler, J.
+(2020).
+The Incubation Period of Coronavirus Disease 2019 (COVID-19) From Publicly Reported Confirmed Cases: Estimation and Application.
+Annals of internal medicine, 172(9), 577–582.
+https://doi.org/10.7326/M20-0504
+
+[3] H. Wickham. ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag New York, 2016.
+
+[4] H. Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686, https://doi.org/10.21105/joss.01686
+
+[5] Angelo Canty and Brian Ripley (2021).
+boot: Bootstrap R (S-Plus) Functions.
+R package version 1.3-28., Davison, A.
+C.
+& Hinkley, D.
+V.
+(1997) Bootstrap Methods and Their Applications.
+Cambridge University Press, Cambridge.
+ISBN 0-521-57391-2

### 2021-12-16 Paper.Rmd
First round of proofreading- fixed some grammar and reduced some wordiness

@@
   #Give incubation time
-  current_suceptable[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5)
+  current_suceptable[newly_infected, 4] <- rpois(n=length(newly_infected), lambda = 5.15)
   #Give recovery time
@@
 Background:
-The paper "Novel approach for Monte Carlo simulation of the new COVID-19 spread dynamics aim's to investigate the transmission and incubation random processes of COVID-19.
-The goal of the study is to generate epidemiological data based on the natural mechanism's of transmission of the virus assuming random interactions of a large-finite number of individuals in very short distance ranges.
-A few important assumptions that were made were in how the transmission of the virus occurs when the physical distance between individuals decreases to where the probability of transmission converges to one, asymptotically.
-Their model defined the steps of movement in a defined space as a randomly assigned process.
-They approached this through the SIR model; A model defining Susceptible, Infected, Recovered individuals.
+The paper "Novel approach for Monte Carlo simulation of the new COVID-19 spread dynamics" aims to investigate the transmission and incubation random processes of Covid-19.
+The goal of the study is to generate epidemiological data based on the natural mechanisms of transmission of the virus assuming random interactions of a large-finite number of subjects in very short distances.
+A few important assumptions were made in how the transmission of the virus occurs when the physical distance between subjects decreases, so that the probability of transmission converges to one as the distance between subjects goes to zero.
+Their model defined the steps of movement in a defined space as a random process.
+They approached this through the SIR model; A model defining Susceptible, Infected, and Recovered individuals.
 All change in the SIR model is based on time, as the function iterates through a set number of days.
-They started with a 0.5% infection rate and simulation daily infection counts over a range of time.
-In order to capture many factors in the transmission including the relationship between infection probability between physical distance, effective and ineffective mask wearing, and environmental conditions they distributed these factors Exponential(rate = lambda).
-Initial recovery and incubation times were distributed Gamma(alpha,beta).
-(Source 1)
+They started with a 0.5% infection rate and simulate daily infection counts over a number of days.
+In order to capture the many factors in transmission, including the relationship between infection probability and physical distance, effective and ineffective mask wearing, and environmental conditions they distributed these factors Exponential(rate = lambda).
+Initial recovery and incubation times were distributed Gamma($\alpha$, $\beta$) [1].
 
@@
 The motivation behind our Monte Carlo Covid-19 simulator is to be able to better understand the spread of Covid-19.
-Through Monte Carlo simulation, we can observe what affect variables such as starting infected population, total population, physical space, infection distance, as well as incubation and recovery times have on the long term spread of the disease.
+Through Monte Carlo simulation, we can observe what affect variables such as starting infected population, total population, physical space, infection distance (affected by masks), level of population vaccination, as well as incubation and recovery times have on the spread of the disease.
 These variables can be easily adjusted in our code to give different scenarios.
@@
 This can be well visualized in a plot giving number of infected people per day.
-At the beginning of the Covid-19 pandemic, there were public health measures put into place that aimed at 'flattening' the curve of daily cases of Covid-19.
+At the beginning of the Covid-19 pandemic, there were public health measures put into place that aimed at 'flattening' the curve of daily case counts of Covid-19.
 We are interested in seeing what effect different policies and population characteristics have on the plot of daily Covid-19 infections.
@@
 To start, we created functions that generate a random step length.
-This was done using the rnorm() function for the normal distribution with a mean and standard deviation of the minimum of the dimensions divided by four and twelve respectively.
-Once we have a step length we generate a step direction from a uniform(0, 2$\pi$) distribution using runif().
-This gives the direction angle in radians.
+This was done using the rnorm function for the normal distribution with a mean and standard deviation of the minimum of the dimensions divided by four and twelve respectively.
+Once we have a step length we generate a step direction from a uniform(0, 2$\pi$) distribution using runif.
+This gives the movement direction angle in radians.
 From these two pieces of information, we can then update the coordinate values in the update_coords function by adding the change to the original x and y values.
@@
 
-The obvious problem that arises when using this approach is that subjects will inevitably leave the specified space they are supposed to remain in.
-For example, if we want the subjects to stay in a [0, 1] x [0, 1] square, and we let them move in any direction, the mean step distance will be 0.25, so it would only take a centered subject a couple moves in the same direction before they leave the space.
-The solution we employed was to check and see whether a certain move would put a subject out of bounds, and if so re-sample a different move, then repeat for all subjects until they are all within bounds.
-This is what the coord_checker() function does.
+The problem that arises when using this approach is that subjects will inevitably leave the specified space they are supposed to remain in.
+The solution to this problem is given in the coord_checker function.
+For example, if we want the subjects to stay in a [0, 1] x [0, 1] square, and let them move in any direction, the mean step distance will be 0.25, so it would only take a centered subject a couple moves in the same direction before they leave the space.
+The solution we employed was to check and see whether a certain move would put a subject out of bounds, and if so, re-sample a different move.
+Then repeat this process for all subjects until they are all within bounds.
 
 After moving the subjects randomly in the given space, the next step in the simulation is to check if any infected subjects have infected others.
-This is done via the infection_status() function.
+This is done via the infection_status function.
 The first thing we did was subset the subjects into different data frames by infection status.
 Then we can check how far the susceptible subjects are from the infected subjects.
-If they come within a crucial distance generated using an exponential distribution, then they are vulnerable to infection.
-Then if the susceptible person is vaccinated, we generate a binomial(1, 0.8) random variable to determine if the vaccine was effective in preventing infection.
+If they come within a crucial distance generated using an exponential distribution with the passed in mean crucial distance, then they are vulnerable to infection.
+If the susceptible person is vaccinated, we generate a binomial(1, 0.8) random variable to determine if the vaccine was effective in preventing infection.
+We chose 0.8 to be the likelihood the vaccine protects the susceptible subject against infection.
 The third condition necessary for infection to occur is that the incubation period of the virus has passed for the infected person.
-The incubation length is assigned upon infection using rpois(1, 5), and decreases by one each day until it reaches zero.
-If binomial vaccine effect returns false, and the susceptible person is within the generated crucial distance of the infected person, and the infected person is past the incubation period, then the suceptible person becomes infected.
-Once infected, a subject is assigned a recovery time using rpois(1, 14).
+The incubation length is assigned upon infection using rpois(1, 5.15), and decreases by one each day until it reaches zero.
+If binomial vaccine effect returns false, and the susceptible person is within the generated crucial distance of the infected person, and the infected person is past the incubation period, then the susceptible person becomes infected.
+Once infected, a subject is assigned a recovery time using round(rgamma(1, 6, 2/3)).
 For each iteration in the simulator, one is subtracted from the recovery time.
@@
 All the above culminates in the simulator function.
-This function takes in the given area, number of subjects, number of starting infected subjects, mean infection distance, number of days for the simulation, and proportion of subjects that are vaccinated.
+This function takes in the given area, number of subjects, number of starting infected subjects, mean infection distance, number of days for the simulation, and proportion of subjects that are vaccinated as arguments.
 Using a for loop for each day, the function generates new positions for the subjects, and returns how many people have been infected per day.
@@
 This is done in the get_bootstrap_cis function.
-The function then returns the bootstrap confidence intervals as well as the mean for each day for a given sample size.
+The function returns the bootstrap confidence intervals as well as the mean for each day, for a given sample size.
 For our purposes we used a sample size of 20 due to the computational burden of repeatedly running simulations.
@@
 Results:
-Going to look at 1x1 with 1000 people: represents small town population density with 0.5% intial infected.
-Will look at distances between 0.001 (6 ft) to 0.01 (60 ft?) and see what differences exist.
-Assuming no vaccinations.
-```{r, cache=TRUE}
+
+```{r, cache=TRUE, echo=FALSE}
 set.seed(400)
@@
 We started with 5 infected people in each simulation.
-In our first two simulations we were attempting to simulate a 6 and 26 foot infection distance.
-As you can see from the first two plots above, no one was infected from the 5 initial people who were infected.
-This is because in these examples we were trying to simulate a small town with a low population density.
+In our first two simulations we were attempting to simulate a 6- and 26- foot infection distance.
+As you can see from the first two plots above, no one was infected from the 5 initial people who were infected for the mean crucial distance of 6 feet.
+For the crucial distance of 26 feet, some people got infected early on, but eventually everyone recovered and the number of infections went to zero.
+This is because in these examples we were attempting to simulate a small town with a low population density.
 This is supposed to represent 1000 people in a town that is 36 million square feet or about 1.3 square miles.
-Since the population density is so low, it is extremely unlikely for two people to come in close enough contact to contract Covid-19 in our simulation.
-Our simulation does have its limitations and this may not be realistic.
+Since the population density is low, it is unlikely for two people to come in close enough contact to contract Covid-19 in our simulation.
+This is a scenario in which our simulator might not be realistic.
 Our simulator is assuming every person is independent and randomly moves around from day to day.
-This doesn't account for hanging out with friends or going home to your family which are common situations where contracting Covid-19 is much more likely.
-Accounting for these factors might be possible, but its beyond the scope of this project.
+This doesn't account for seeing friends or going home to your family, which are common situations where contracting Covid-19 is more likely.
+Accounting for these factors might be possible, but it's beyond the scope of this project.
 In our third simulation, we used a bootstrap confidence interval for an infection distance of about 60 feet.
-This distance was finally large enough that people still got infected despite the low population density.
+This distance was finally large enough so that people still got infected despite the low population density.
 Based on the plot, the number of infected people will peak around 50 days and then slowly decrease as the majority of people start to recover and gain immunity.
@@
 
-Compare different vaccination rates
-```{r}
+```{r, echo=FALSE}
 set.seed(400)
@@
 
-In the previous three simulations we assumed that no one was vaccinated, but we also wanted to look at how a vaccine would effect the spread of Covid-19.
+In the previous three simulations we assumed that no one was vaccinated, but we also wanted to look at how a vaccine would affect the spread of Covid-19.
 In these simulations we looked at 200 people with the same dimension parameters as before, but with only one person initially infected.
@@
 All the parameters were held the same other than the vaccination rate for these simulations.
-The vaccine rates of the four examples were: 0, .5, .8, and .95.
-In the plot that shows the number of infected for each vaccination rate, black is 0 vaccinated, red is .5, blue is .8, and green is .95.
+The vaccine rates of the four examples were: 0, 0.5, 0.8, and 0.95.
+In the plot that shows the number of infected subjects by day for each vaccination rate, the proportion of vaccinated subjects for black is 0 vaccinated, red is 0.5, blue is 0.8, and green is 0.95.
 As we would expect, when no one is vaccinated, the number of infected people peaks and falls much faster than when some people are vaccinated.
 It only took around 15 days to peak and nearly everyone was recovered by day 30.
-When no one was vaccinated it took much less time to get sick, but people also were recovered faster because everyone already had the virus.
-This is the idea of herd immunity that is often talked about, but it poses a massive problem with the hospitals.
-If everyone gets sick in a short period of time, hospitals can get overwhelmed and the death tolls can skyrocket due to lack of equipment and staff.
-Vaccinations aren't perfect, but they can help flatten the curve so the infection numbers don't peak as fast and also reduce the severity of the symptoms so less people need to be hospitalized.
-It is still possible to contract Covid-19 while vaccinated, but it is much less likely.
+When no one was vaccinated it took much less time to get sick, but people also recovered faster because everyone already had the virus.
+This is the idea of herd immunity that is often talked about, but it poses a problem for hospitals.
+If everyone gets sick in a short period of time, hospitals can become overwhelmed and the death tolls can skyrocket due to lack of equipment and staff.
+Vaccinations are not perfect, accounted for in our simulator by using a binomial random variable to see if effective, but they can help flatten the curve so the infection numbers don't peak as fast.
+It is still possible to contract Covid-19 while vaccinated, but it is less likely than otherwise.
 As you can see in the last plot, as the vaccination rate increased, the longer it took for the cases to peak.
-The peak was also much lower than when no one was vaccinated and it took longer for the cases to completely disappear since people were being infected slower.
-This shows that a higher vaccination rate helps slow down the spread of Covid-19 even if it can't completely prevent it.
+The peak was also lower than when no one was vaccinated, and it took longer for the cases to completely disappear since people were being infected slower.
+This shows that a higher vaccination rate helps slow down the spread of Covid-19 even if it cannot completely prevent it.
 

### 2021-12-16 Paper.Rmd
small spelling changes

@@
 They approached this through the SIR model; A model defining Susceptible, Infected, and Recovered individuals.
-All change in the SIR model is based on time, as the function iterates through a set number of days.
-They started with a 0.5% infection rate and simulate daily infection counts over a number of days.
+Any change in the SIR model is based on time, as the function iterates through a set number of days.
+They started with a 0.5% infection rate and simulated daily infection counts over a number of days.
 In order to capture the many factors in transmission, including the relationship between infection probability and physical distance, effective and ineffective mask wearing, and environmental conditions they distributed these factors Exponential(rate = lambda).
@@
 The motivation behind our Monte Carlo Covid-19 simulator is to be able to better understand the spread of Covid-19.
-Through Monte Carlo simulation, we can observe what affect variables such as starting infected population, total population, physical space, infection distance (affected by masks), level of population vaccination, as well as incubation and recovery times have on the spread of the disease.
+Through Monte Carlo simulation, we can observe what affect variables such as starting infected population, total population, physical space, infection distance (affected by masks), level at which the population is vaccinated, as well as incubation and recovery times have on the spread of the disease.
 These variables can be easily adjusted in our code to give different scenarios.

### 2021-12-16 Paper.Rmd
Fixed plot code

@@
 ggplot() +
-  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
-  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
-  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red') + 
+  geom_line(aes(x=1:151, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
+  geom_line(aes(x=1:151, y=plot_dat[ ,2])) +
+  geom_line(aes(x=1:151, y=plot_dat[ ,3]), linetype = 2, color = 'red') + 
   labs(x="Day", y="People infected")

### 2021-12-16 Paper.Rmd
Removed time checker for bootstrap
Added titles to plots

--- 2021-12-16 Paper.Rmd
@@
     samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist, prop_vac)
-    print(i)
   }
@@
   ylab('Number of Cases') +
-  ggtitle('Number of Covid-19 cases over time')
+  ggtitle('Number of Covid-19 Cases Over Time')
 
@@
 ggplot() +
-  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
-  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
-  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red') + 
-  labs(x="Day", y="People infected")
+  geom_line(aes(x=1:151, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
+  geom_line(aes(x=1:151, y=plot_dat[ ,2])) +
+  geom_line(aes(x=1:151, y=plot_dat[ ,3]), linetype = 2, color = 'red') + 
+  labs(x="Day", y="People infected") +
+  ggtitle('Covid-19 Cases by Day')
 
@@
   geom_line(aes(x=1:51, y=plot_dat1[ ,3]), linetype = 2, color = 'red') + 
-  labs(x="Day", y="People infected")
+  labs(x="Day", y="People infected") +
+  ggtitle('Covid-19 Cases by Day')
 
@@
   geom_line(aes(x=1:51, y=plot_dat2[ ,3]), linetype = 2, color = 'red') + 
-  labs(x="Day", y="People infected")
+  labs(x="Day", y="People infected") +
+  ggtitle('Covid-19 Cases by Day')
 
@@
   geom_line(aes(x=1:51, y=plot_dat3[ ,3]), linetype = 2, color = 'red') + 
-  labs(x="Day", y="People infected")
+  labs(x="Day", y="People infected") +
+  ggtitle('Covid-19 Cases by Day')
 
@@
   geom_line(aes(x=1:51, y=plot_dat4[ ,3]), linetype = 2, color = 'red') + 
-  labs(x="Day", y="People infected")
+  labs(x="Day", y="People infected") +
+  ggtitle('Covid-19 Cases by Day')
 
@@
   geom_line(aes(x=1:51, y=plot_dat4[ ,2]), color='green') + 
-  labs(x="Day", y="People infected")
+  labs(x="Day", y="People infected") +
+  ggtitle('Covid-19 Cases by Day')
 

### 2021-12-16 Paper.Rmd
Made some minor adjustments

@@
 The paper "Novel approach for Monte Carlo simulation of the new COVID-19 spread dynamics" aims to investigate the transmission and incubation random processes of Covid-19.
-The goal of the study is to generate epidemiological data based on the natural mechanisms of transmission of the virus assuming random interactions of a large-finite number of subjects in very short distances.
-A few important assumptions were made in how the transmission of the virus occurs when the physical distance between subjects decreases, so that the probability of transmission converges to one as the distance between subjects goes to zero.
+The goal of the study is to generate epidemiological data based on the natural mechanisms of transmission of Covid-19 assuming random interactions between subjects.
+A few important assumptions were made in how the transmission of Covid-19 occurs when the physical distance between subjects decreases, so that the probability of transmission converges to one as the distance between subjects goes to zero.
 Their model defined the steps of movement in a defined space as a random process.
@@
 The function returns the bootstrap confidence intervals as well as the mean for each day, for a given sample size.
-For our purposes we used a sample size of 20 due to the computational burden of repeatedly running simulations.
+For our purposes we used sample sizes of 20 and 30 due to the computational burden of repeatedly running simulations.
 This data can be used to create a plot of the mean number of cases per day as well as 95% bootstrap confidence intervals for each day.
@@
 set.seed(400)
-plot_dat1 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=20, prop_vac = 0)
+plot_dat1 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=30, prop_vac = 0)
 
@@
 
-plot_dat2 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=20, prop_vac = 0.5)
+plot_dat2 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=30, prop_vac = 0.5)
 
@@
 
-plot_dat3 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=20, prop_vac = 0.8)
+plot_dat3 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=30, prop_vac = 0.8)
 
@@
 
-plot_dat4 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=20, prop_vac = 0.95)
+plot_dat4 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=30, prop_vac = 0.95)
 

### 2021-12-16 Stat 400 presentation.Rmd
Made some minor adjustments

@@
 
-- The goal of the study is to generate epidemiological data based on the natural mechanism's of transmission of the virus assuming random interactions of a large-finite number of individuals in very short distance ranges.
+- The goal of the study is to generate epidemiological data based on the natural mechanisms of transmission of the virus assuming random interactions of subjects in a confined space.
 
@@
 
-- The transmission of the virus occurs when the physical distance between individuals decreases to where the probability of transmission converges to one, asymptotmically.
+- The transmission of the virus occurs when the physical distance between individuals decreases to where the probability of transmission converges to one, as the distance between subjects goes to zero.
 
-- the step of movement of people is a randomly assigned process.
+- The step of movement of people is a randomly assigned process.
 
-- the specific parameters of focus will be recovery and incubation time.
+- The specific parameters of focus will be recovery and incubation time.
 

### 2021-12-16 Stat 400 proj.Rmd
Wrote about the simulator function
Readme updated

@@
 knitr::opts_chunk$set(echo = TRUE)
-#testing github
 library(tidyverse)
@@
 ```{r}
-simulator22 <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist){
-  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
+simulator22 <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, prop_vac){
+  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0, prop_vac = prop_vac)
   end_day <- list()
@@
 }
-days <- simulator22(20, 5, 1, 1, 1, 0.2)
+days <- simulator22(20, 5, 1, 1, 1, 0.2, 0)
 days
